### 2019-07-19 draft_conference_paper.tex
being lazy

%%%%%%%%%%%%%%%%%%%%%%%%%%% asme2e.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for producing ASME-format articles using LaTeX            %
% Written by   Harry H. Cheng                                        %
%              Integration Engineering Laboratory                    %
%              Department of Mechanical and Aeronautical Engineering %
%              University of California                              %
%              Davis, CA 95616                                       %
%              Tel: (530) 752-5020 (office)                          %
%                   (530) 752-1028 (lab)                             %
%              Fax: (530) 752-4158                                   %
%              Email: hhcheng@ucdavis.edu                            %
%              WWW:   http://iel.ucdavis.edu/people/cheng.html       %
%              May 7, 1994                                           %
% Modified: February 16, 2001 by Harry H. Cheng                      %
% Modified: January  01, 2003 by Geoffrey R. Shiflett                %
% Use at your own risk, send complaints to /dev/null                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% use twocolumn and 10pt options with the asme2e format
\documentclass[twocolumn,10pt]{asme2e}
\special{papersize=8.5in,11in}

%% The class has several options
%  onecolumn/twocolumn - format for one or two columns per page
%  10pt/11pt/12pt - use 10, 11, or 12 point font
%  oneside/twoside - format for oneside/twosided printing
%  final/draft - format for final/draft copy
%  cleanfoot - take out copyright info in footer leave page number
%  cleanhead - take out the conference banner on the title page
%  titlepage/notitlepage - put in titlepage or leave out titlepage
%  
%% The default is oneside, onecolumn, 10pt, final

%%% Replace here with information related to your conference
\confshortname{IDETC/CIE 2009}
\conffullname{the ASME 2009 International Design Engineering Technical Conferences \&\\
              Computers and Information in Engineering Conference}

%%%%% for date in a single month, use
%\confdate{24-28}
%\confmonth{September}
%%%%% for date across two months, use
\confdate{August 30-September 2}
\confyear{2009}
\confcity{San Diego}
\confcountry{USA}

%%% Replace DETC2009/MESA-12345 with the number supplied to you 
%%% by ASME for your paper.
\papernum{DETC2009/MESA-12345}

%%% You need to remove 'DRAFT: ' in the title for the final submitted version.
\title{DRAFT: AN ARTICLE CREATED USING \LaTeX2\raisebox{-.3ex}{$\epsilon$}\ IN ASME FORMAT}
%%% for the discussion section only
%\usepackage{helvet}
%\title{\fontfamily{phv}\selectfont{\Huge{DRAFT: AN ARTICLE CREATED USING \LaTeX2\raisebox{-.3ex}{$\epsilon$}\ IN ASME FORMAT}}}

%%% first author
\author{Prashanth Irudayaraj
    \affiliation{
	Research Manager\\
	Keep Network\\
    Email: prashanth@keep.network
    }	
}

%%% second author
%%% remove the following entry for single author papers
%%% add more entries for additional authors
\author{Antonio Cordozo\thanks{Address all correspondence to this author.} \\
       {\tensfb Second Coauthor}     
    \affiliation{Department or Division Name\\
	Keep Network\\
	antonio@keep.network
	}

\author{Tilde Uusalito\thanks{Address all correspondence to this author.} \\
	{\tensfb Second Coauthor}     
 \affiliation{Department or Division Name\\
 Keep Network\\
 promethea@keep.network
 }

 \author{Tilde Uusalito\thanks{Address all correspondence to this author.} \\
	{\tensfb Second Coauthor}     
 \affiliation{Department or Division Name\\
 Keep Network\\
 promethea@keep.network
 }
}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{\it This article illustrates preparation of ASME paper using \LaTeX2\raisebox{-.3ex}{$\epsilon$}. An abstract for an ASME paper should be less than 150 words and is normally in italics.}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{nomenclature}
\entry{A}{You may include nomenclature here.}
\entry{$\alpha$}{There are two arguments for each entry of the nomemclature environment, the symbol and the definition.}
\end{nomenclature}

The spacing between abstract and the text heading is two line spaces.  The primary text heading is  boldface in all capitals, flushed left with the left margin.  The spacing between the  text and the heading is also two line spaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{INTRODUCTION}

This article illustrates preparation of ASME paper using \LaTeX2\raisebox{-.3ex}{$\epsilon$}. The \LaTeX\  macro \verb+asme2e.cls+, the {\sc Bib}\TeX\ style file \verb+asmems4.bst+, and the template \verb+asme2e.tex+ that create this article are available on the WWW  at the URL address \verb+http://iel.ucdavis.edu/code/+. To ensure compliance with the 2003 ASME MS4 style guidelines  \cite{asmemanual}, you should modify neither the \LaTeX\ macro \verb+asme2e.cls+ nor the {\sc Bib}\TeX\ style file \verb+asmems4.bst+. By comparing the output generated by typesetting this file and the \LaTeX2\raisebox{-.3ex}{$\epsilon$} source file, you should find everything you need to help you through the preparation of ASME paper using \LaTeX2\raisebox{-.3ex}{$\epsilon$}. Details on using \LaTeX\ can be found in \cite{latex}. Instructions for submitting an electronic version of a paper via ftp for publication on CD-ROM or online  are given at the URL address \verb+http://www.asme.org/pubs/submittal.html+.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{VERY VERY VERY VERY VERY VERY VERY VERY LONG HEADING}

If the heading should run into more than one line, the run-over is flush left.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Second-Level Heading}

The next level of heading is boldface with upper and lower case letters. The heading is flushed left with the left margin. The spacing to the next heading is two line spaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Third-Level Heading.}

The third-level of heading follows the style of the second-level heading, but it is indented and followed by a period, a space, and the start of corresponding text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{PAPER NUMBER}

ASME assigns each accepted paper with a unique number. Replace {\bf DETC98/DAC-1234} in the input file preamble (the location will be obvious) with the paper number supplied to you  by ASME for your paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{USE OF SI UNITS}

An ASME paper should use SI units.  When preference is given to SI units, the U.S. customary units may be given in parentheses or omitted. When U.S. customary units are given preference, the SI equivalent {\em shall} be provided in parentheses or in a supplementary table. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{MATHEMATICS}

Equations should be numbered consecutively beginning with (1) to the end of the paper, including any appendices.  The number should be enclosed in parentheses and set flush right in the column on the same line as the equation.  An extra line of space should be left above and below a displayed equation or formula. \LaTeX\ can automatically keep track of equation numbers in the paper and format almost any equation imaginable. An example is shown in Eqn.~(\ref{eq_ASME}). The number of a referenced equation in the text should be preceded by Eqn.\ unless the reference starts a sentence in which case Eqn.\ should be expanded to Equation.

\begin{equation}
f(t) = \int_{0_+}^t F(t) dt + \frac{d g(t)}{d t}
\label{eq_ASME}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{FIGURES AND TABLES}

All figures should be positioned at the top of the page where possible.  All figures should be numbered consecutively and captioned; the caption uses all capital letters, and centered under the figure as shown in Fig.~\ref{figure_ASME}. All text within the figure should be no smaller than 7~pt. There should be a minimum two line spaces between figures and text. The number of a referenced figure or table in the text should be preceded by Fig.\ or Tab.\ respectively unless the reference starts a sentence in which case Fig.\ or Tab.\ should be expanded to Figure or Table.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% begin figure %%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\setlength{\unitlength}{0.012500in}%
\begin{picture}(115,35)(255,545)
\thicklines
\put(255,545){\framebox(115,35){}}
\put(275,560){Beautiful Figure}
\end{picture}
\end{center}
\caption{THE FIGURE CAPTION USES CAPITAL LETTERS.}
\label{figure_ASME} 
\end{figure}
%%%%%%%%%%%%%%%% end figure %%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% begin table   %%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
\caption{THE TABLE CAPTION USES CAPITAL LETTERS, TOO.}
\begin{center}
\label{table_ASME}
\begin{tabular}{c l l}
& & \\ % put some space after the caption
\hline
Example & Time & Cost \\
\hline
1 & 12.5 & \$1,000 \\
2 & 24 & \$2,000 \\
\hline
\end{tabular}
\end{center}
\end{table}
%%%%%%%%%%%%%%%% end table %%%%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All tables should be numbered consecutively and  captioned; the caption should use all capital letters, and centered above the table as shown in Table~\ref{table_ASME}. The body of the table should be no smaller than 7 pt.  There should be a minimum two line spaces between tables and text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{FOOTNOTES\protect\footnotemark}
\footnotetext{Examine the input file, asme2e.tex, to see how a footnote is given in a head.}

Footnotes are referenced with superscript numerals and are numbered consecutively from 1 to the end of the paper\footnote{Avoid footnotes if at all possible.}. Footnotes should appear at the bottom of the column in which they are referenced.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{CITING REFERENCES}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The ASME reference format is defined in the authors kit provided by the ASME.  The format is:

\begin{quotation}
{\em Text Citation}. Within the text, references should be cited in  numerical order according to their order of appearance.  The numbered reference citation should be enclosed in brackets.
\end{quotation}

The references must appear in the paper in the order that they were cited.  In addition, multiple citations (3 or more in the same brackets) must appear as a `` [1-3]''.  A complete definition of the ASME reference format can be found in the  ASME manual \cite{asmemanual}.

The bibliography style required by the ASME is unsorted with entries appearing in the order in which the citations appear. If that were the only specification, the standard {\sc Bib}\TeX\ unsrt bibliography style could be used. Unfortunately, the bibliography style required by the ASME has additional requirements (last name followed by first name, periodical volume in boldface, periodical number inside parentheses, etc.) that are not part of the unsrt style. Therefore, to get ASME bibliography formatting, you must use the \verb+asmems4.bst+ bibliography style file with {\sc Bib}\TeX. This file is not part of the standard BibTeX distribution so you'll need to place the file someplace where LaTeX can find it (one possibility is in the same location as the file being typeset).

With \LaTeX/{\sc Bib}\TeX, \LaTeX\ uses the citation format set by the class file and writes the citation information into the .aux file associated with the \LaTeX\ source. {\sc Bib}\TeX\ reads the .aux file and matches the citations to the entries in the bibliographic data base file specified in the \LaTeX\ source file by the \verb+\bibliography+ command. {\sc Bib}\TeX\ then writes the bibliography in accordance with the rules in the bibliography .bst style file to a .bbl file which \LaTeX\ merges with the source text.  A good description of the use of {\sc Bib}\TeX\ can be found in \cite{latex, goosens} (see how 2 references are handled?).  The following is an example of how three or more references \cite{latex, asmemanual,  goosens} show up using the \verb+asmems4.bst+ bibliography style file in conjunction with the \verb+asme2e.cls+ class file. Here are some more \cite{art, blt, ibk, icn, ips, mts, mis, pro, pts, trt, upd} which can be used to describe almost any sort of reference.

% Here's where you specify the bibliography style file.
% The full file name for the bibliography style file 
% used for an ASME paper is asmems4.bst.
\bibliographystyle{asmems4}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgment}
Thanks go to D. E. Knuth and L. Lamport for developing the wonderful word processing software packages \TeX\ and \LaTeX. I also would like to thank Ken Sprott, Kirk van Katwyk, and Matt Campbell for fixing bugs in the ASME style file \verb+asme2e.cls+, and Geoff Shiflett for creating 
ASME bibliography stype file \verb+asmems4.bst+.
\end{acknowledgment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The bibliography is stored in an external database file
% in the BibTeX format (file_name.bib).  The bibliography is
% created by the following command and it will appear in this
% position in the document. You may, of course, create your
% own bibliography by using thebibliography environment as in
%
% \begin{thebibliography}{12}
% ...
% \bibitem{itemreference} D. E. Knudsen.
% {\em 1966 World Bnus Almanac.}
% {Permafrost Press, Novosibirsk.}
% ...
% \end{thebibliography}

% Here's where you specify the bibliography database file.
% The full file name of the bibliography database for this
% article is asme2e.bib. The name for your database is up
% to you.
\bibliography{asme2e}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix       %%% starting appendix
\section*{Appendix A: Head of First Appendix}
Avoid Appendices if possible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix B: Head of Second Appendix}
\subsection*{Subsection head in appendix}
The equation counter is not reset in an appendix and the numbers will
follow one continual sequence from the beginning of the article to the very end as shown in the following example.
\begin{equation}
a = b + c.
\end{equation}

\end{document}

### 2019-07-19 Mesa Simulations/agent.py

@@ -151,7 +151,6 @@ class Signature(Agent):
         self.model.newest_signature_id +=1 #increments the signature ID by one after a new signature is created
         self.signature_process_complete = False
         self.block_delay_complete = False
-        self.dominator_id = -1
         self.dominator_percent = 0
         self.offline_percent = 0
         self.signature_failure = False
@@ -187,9 +186,6 @@ class Signature(Agent):
         self.offline_percent = sum(failed_list)/sum(self.ownership_distr)
         self.dominator_percent = (sum(failed_list) + max(self.ownership_distr))/sum(self.group.ownership_distr) # adds the failed node virtual stakers and max node virtual stakers
         self.signature_failure = (sum(failed_list)+max(self.ownership_distr)) > (1-self.model.max_malicious_threshold)
-
-        if self.dominator_percent*100 > self.model.max_malicious_threshold:
-            self.dominator_id = np.argmax(self.ownership_distr)
 
         # calculate misbehaving nodes
     

### 2019-07-19 Mesa Simulations/model.py

@@ -210,7 +210,7 @@ class Beacon_Model(Model):
             if signature.type == "signature":
                 total_signatures +=1
                 dominator_array.append(signature.dominator_percent)
-                dominator_count += (signature.dominator_id>=0)
+                dominator_count += (signature.dominator_percent>=self.max_malicious_threshold)
                 failed_signatures += (signature.offline_percent>=self.failed_signature_threshold)
 
         self.perc_failed_signatures = failed_signatures/(total_signatures+0.00000000000000001)

### 2019-07-22 Mesa Simulations/agent.py
changed node failure to connection_failure

@@ -21,9 +21,9 @@ class Node(Agent):
         self.connection_delay = np.random.randint(0,node_connection_delay) #uniform randomly assigned connection delay step value
         self.mainloop_fork_delay = np.random.randint(0,node_mainloop_connection_delay) #uniform randomly assigned connection delay step value
         self.timer = self.model.timer
-        self.node_failure_percent = failure_percent
+        self.node_connection_failure_percent = failure_percent
         self.node_death_percent = death_percent
-        self.failure = False
+        self.connection_failure = False
         self.death = False
         self.dkg_misbehaving = False
         self.malicious = np.random.randint (0,100) < misbehaving_nodes  # sets the node as malicious baed on the misbehaving % in model parameters
@@ -41,7 +41,7 @@ class Node(Agent):
                 self.mainloop_status = "forked"
             
         #simulate node failure
-        self.failure = np.random.randint(0,100) < self.node_failure_percent
+        self.connection_failure = np.random.randint(0,100) < self.node_connection_failure_percent
         self.death = np.random.randint (0,100) < self.node_death_percent
 
         #disconnect the node if failure occurs

### 2019-07-22 Mesa Simulations/agent.py
removed mainloop and staked status

@@ -16,8 +16,6 @@ class Node(Agent):
         self.num_tickets = int(tickets)
         self.ticket_list = []
         self.connection_status = "not connected" #change later to event - currently used for node failure process
-        self.mainloop_status = "not forked"
-        self.stake_status = "not staked"
         self.connection_delay = np.random.randint(0,node_connection_delay) #uniform randomly assigned connection delay step value
         self.mainloop_fork_delay = np.random.randint(0,node_mainloop_connection_delay) #uniform randomly assigned connection delay step value
         self.timer = self.model.timer
@@ -34,11 +32,6 @@ class Node(Agent):
             self.connection_delay -=1
         else:
             self.connection_status = "connected"
-        #once connected fork the main loop
-            if self.mainloop_fork_delay>0:
-                self.mainloop_fork_delay -=1
-            else: 
-                self.mainloop_status = "forked"
             
         #simulate node failure
         self.connection_failure = np.random.randint(0,100) < self.node_connection_failure_percent

### 2019-07-22 Mesa Simulations/model.py

@@ -55,7 +55,7 @@ class Beacon_Model(Model):
              "Failed Singature %" : "perc_failed_signatures" },
             agent_reporters={"Type_ID": lambda x : x.node_id if x.type == "node" else ( x.group_id if x.type == "group" else x.signature_id) , 
             "Type" : "type",
-            "Node Status (Connection_Mainloop_Stake)": lambda x : str(x.connection_status + x.mainloop_status + x.stake_status) if x.type == "node" else None,
+            "Node Status (Connection_Mainloop_Stake)": lambda x : str(x.connection_status) if x.type == "node" else None,
             "Status": lambda x: x.status if x.type == "group" or x.type == "signature" else None, 
             "Malicious": lambda x : x.malicious if x.type == "node" else None,
             "DKG Block Delay" : lambda x : x.dkg_block_delay if x.type =="group" else None,
@@ -179,7 +179,7 @@ class Beacon_Model(Model):
         temp_active_nodes = [] #take out later - id of active nodes
         for agent in self.schedule.agents:
             if agent.type == "node":
-                if agent.mainloop_status == "forked": 
+                if agent.connection_status == "connected": 
                     temp_active_node_list.append(agent) #adds the node to the active list only if it is in the forked state
                     temp_active_nodes.append(agent.node_id)
                 

### 2019-07-22 Mesa Simulations/agent.py
changed to group.ownership_distr

@@ -28,21 +28,21 @@ class Node(Agent):
     
     def step(self):
         #connect to chain
-        if self.connection_delay>0:
-            self.connection_delay -=1
-        else:
-            self.connection_status = "connected"
-            
-        #simulate node failure
-        self.connection_failure = np.random.randint(0,100) < self.node_connection_failure_percent
-        self.death = np.random.randint (0,100) < self.node_death_percent
-
         #disconnect the node if failure occurs
         if self.failure or self.death:
             self.node_disconnect()
+        else:
+            if self.connection_delay>0:
+                self.connection_delay -=1
+            else:
+                self.connection_status = "connected"
+                
+            #simulate node failure
+            self.connection_failure = np.random.randint(0,100) < self.node_connection_failure_percent
+            self.death = np.random.randint (0,100) < self.node_death_percent
 
-        #refresh active nodes list
-        self.model.refresh_connected_nodes_list()
+            #refresh active nodes list
+            self.model.refresh_connected_nodes_list()
 
     def advance(self):
         pass
@@ -176,7 +176,7 @@ class Signature(Agent):
                         temp_signature_distr[i] = node_tickets
         self.ownership_distr = temp_signature_distr
         failed_list = np.array(self.group.ownership_distr)-np.array(self.ownership_distr)
-        self.offline_percent = sum(failed_list)/sum(self.ownership_distr)
+        self.offline_percent = sum(failed_list)/sum(self.group.ownership_distr)
         self.dominator_percent = (sum(failed_list) + max(self.ownership_distr))/sum(self.group.ownership_distr) # adds the failed node virtual stakers and max node virtual stakers
         self.signature_failure = (sum(failed_list)+max(self.ownership_distr)) > (1-self.model.max_malicious_threshold)
 

### 2019-07-22 Mesa Simulations/agent.py
removed failed nodes from signature failure calc

@@ -178,7 +178,7 @@ class Signature(Agent):
         failed_list = np.array(self.group.ownership_distr)-np.array(self.ownership_distr)
         self.offline_percent = sum(failed_list)/sum(self.group.ownership_distr)
         self.dominator_percent = (sum(failed_list) + max(self.ownership_distr))/sum(self.group.ownership_distr) # adds the failed node virtual stakers and max node virtual stakers
-        self.signature_failure = (sum(failed_list)+max(self.ownership_distr)) > (1-self.model.max_malicious_threshold)
+        self.signature_failure = max(self.ownership_distr) > (1-self.model.max_malicious_threshold)
 
         # calculate misbehaving nodes
     

### 2019-07-22 Mesa Simulations/agent.py
added "percent" to max_malicious_threshold

@@ -178,7 +178,7 @@ class Signature(Agent):
         failed_list = np.array(self.group.ownership_distr)-np.array(self.ownership_distr)
         self.offline_percent = sum(failed_list)/sum(self.group.ownership_distr)
         self.dominator_percent = (sum(failed_list) + max(self.ownership_distr))/sum(self.group.ownership_distr) # adds the failed node virtual stakers and max node virtual stakers
-        self.signature_failure = max(self.ownership_distr) > (1-self.model.max_malicious_threshold)
+        self.signature_failure = max(self.ownership_distr) > (1-self.model.max_malicious_threshold_percent)
 
         # calculate misbehaving nodes
     

### 2019-07-22 Mesa Simulations/model.py

@@ -9,7 +9,7 @@ import numpy as np
 class Beacon_Model(Model):
     """The model"""
     def __init__(self, nodes, ticket_distribution, active_group_threshold, 
-    group_size, max_malicious_threshold, group_expiry, 
+    group_size, max_malicious_threshold_percent, group_expiry, 
     node_failure_percent, node_death_percent,
     signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
     log_filename, run_number, misbehaving_nodes, dkg_block_delay, compromised_threshold,
@@ -23,7 +23,7 @@ class Beacon_Model(Model):
         self.num_active_nodes = 0
         self.inactive_nodes = []
         self.active_group_threshold = active_group_threshold # number of groups that will always be maintained in an active state
-        self.max_malicious_threshold = max_malicious_threshold # threshold above which a signature is deemed to be compromised, typically 51%
+        self.max_malicious_threshold_percent = max_malicious_threshold_percent # threshold above which a signature is deemed to be compromised, typically 51%
         self.group_size = group_size
         self.ticket_distribution = ticket_distribution
         self.newest_id = 0
@@ -210,7 +210,7 @@ class Beacon_Model(Model):
             if signature.type == "signature":
                 total_signatures +=1
                 dominator_array.append(signature.dominator_percent)
-                dominator_count += (signature.dominator_percent>=self.max_malicious_threshold)
+                dominator_count += (signature.dominator_percent>=self.max_malicious_threshold_percent)
                 failed_signatures += (signature.offline_percent>=self.failed_signature_threshold)
 
         self.perc_failed_signatures = failed_signatures/(total_signatures+0.00000000000000001)

### 2019-07-22 Mesa Simulations/agent.py
removed signature failure property from signature

@@ -146,7 +146,6 @@ class Signature(Agent):
         self.block_delay_complete = False
         self.dominator_percent = 0
         self.offline_percent = 0
-        self.signature_failure = False
 
     def step(self):
         #signature
@@ -178,7 +177,6 @@ class Signature(Agent):
         failed_list = np.array(self.group.ownership_distr)-np.array(self.ownership_distr)
         self.offline_percent = sum(failed_list)/sum(self.group.ownership_distr)
         self.dominator_percent = (sum(failed_list) + max(self.ownership_distr))/sum(self.group.ownership_distr) # adds the failed node virtual stakers and max node virtual stakers
-        self.signature_failure = max(self.ownership_distr) > (1-self.model.max_malicious_threshold_percent)
 
         # calculate misbehaving nodes
     

### 2019-07-22 Mesa Simulations/agent.py
corrected dkg compromised calc

@@ -90,8 +90,8 @@ class Group(Agent):
         if self.status == "dkg":
             if self.dkg_block_delay>=0:
                 self.dkg_block_delay -=1 # counts down the block delay
-                # based on DKG process we check for missing/malicious nodes at stage 11
-                if self.dkg_block_delay >=11:
+                # based on DKG process we check for missing/malicious nodes 4 blocks before dkg completes
+                if self.dkg_block_delay == (self.dkg_block_delay - 4):
                     self.offline_percent = self.calculate_offline()/sum(self.ownership_distr) # calculates % nodes offline during dkg
                     self.compromised_percent = self.malicious_percent #+ self.offline_percent
             else:

### 2019-07-22 Mesa Simulations/agent.py
changed from 4 to 3 blocks from completiopn

@@ -91,7 +91,7 @@ class Group(Agent):
             if self.dkg_block_delay>=0:
                 self.dkg_block_delay -=1 # counts down the block delay
                 # based on DKG process we check for missing/malicious nodes 4 blocks before dkg completes
-                if self.dkg_block_delay == (self.dkg_block_delay - 4):
+                if self.dkg_block_delay == (self.dkg_block_delay - 3):
                     self.offline_percent = self.calculate_offline()/sum(self.ownership_distr) # calculates % nodes offline during dkg
                     self.compromised_percent = self.malicious_percent #+ self.offline_percent
             else:

### 2019-07-22 Mesa Simulations/agent.py
initialized group ownership distr as array

@@ -75,7 +75,7 @@ class Group(Agent):
         self.timer = self.model.timer
         self.model.newest_id +=1
         self.model.newest_group_id +=1
-        self.ownership_distr = 0
+        self.ownership_distr = []
         self.malicious_percent = 0
         self.offline_percent = 0
         self.compromised_percent = 0

### 2019-07-22 Mesa Simulations/agent.py
optimizing calc from sum to len

@@ -92,7 +92,7 @@ class Group(Agent):
                 self.dkg_block_delay -=1 # counts down the block delay
                 # based on DKG process we check for missing/malicious nodes 4 blocks before dkg completes
                 if self.dkg_block_delay == (self.dkg_block_delay - 3):
-                    self.offline_percent = self.calculate_offline()/sum(self.ownership_distr) # calculates % nodes offline during dkg
+                    self.offline_percent = self.calculate_offline()/len(self.members) # calculates % nodes offline during dkg
                     self.compromised_percent = self.malicious_percent #+ self.offline_percent
             else:
                 self.status = "active"

### 2019-09-03 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
initial structure

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{A theoretical analysis of the Keep Network random beacon using agent based modeling \\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Prashanth Irudayaraj}
\IEEEauthorblockA{\textit{Keep Network} \\
prashanth@keep.network}

\and
\IEEEauthorblockN{2\textsuperscript{nd} Antonio Cordozo}
\IEEEauthorblockA{\textit{Keep Network} \\
antonio@keep.network}

\and
\IEEEauthorblockN{4\textsuperscript{th} Promethea Raschke}
\IEEEauthorblockA{\textit{Keep Network} \\
promethea@keep.network}

\and
\IEEEauthorblockN{5\textsuperscript{th} Markus Fix}
\IEEEauthorblockA{\textit{Keep Network} \\
markus@keep.network}

\and
\IEEEauthorblockN{6\textsuperscript{th} Liam Zebedee}
\IEEEauthorblockA{\textit{Keep Network} \\
liam@keep.network}
}

\maketitle

\begin{abstract}
    ABM is an effective tool for analysis of complex systems with long term emergent behavior. In this study we apply ABM to analyse the long term behavior of Keep’s random beacon. We look for the emergence of steady state behavior, at which point we evaluate the sensitivity of specific group and signature characteristics to various parameters. The results of this study illustrates the effectiveness of ABM as an aid to the design of novel distributed systems.

\end{abstract}

\begin{IEEEkeywords}
Token Engineering, Agent Based Model, Distributed Systems
\end{IEEEkeywords}

\section{Introduction}

\section{Agent Based Modeling}

Overview of Agent Based Modeling and methods

\section{Analysis of Token based systems}

Discuss the use of ABM for token engineering. Cite recent papers.

\section{Overview of the Keep Random Beacon}

\subsection{Role of the model in the design process}

\subsection{Key research questions}

\section{Model Creation}

\subsection{Terminology}

\subsection{Structure of the Model}
\begin{itemize}

\item Single run
\item Multiple runs

\end{itemize}

\subsection{Assumptions}
\begin{itemize}
\item Stochastic Assumptions
\item Ticket distribution Assumptions
\item Model Assumptions
\end{itemize}

\section{Verification and Validation}
Benchmark using analytical methods - from Promethea

\section{Results}
\begin{itemize}
\item Emergence of steady state behavior
\item Effects of Node failures on group and signature characteristics
\item Effects of stake distributions on group and signature characteristics
\item Additional analyses?
\end{itemize}

\section{Conclusion and Future work}
\begin{itemize}
\item Dynamic systems -Transfer functions instead of stochastic representations?
\item Utility functions
\item Genetic Algorithms
\item Additional questions
\end{itemize}

\end{document}

### 2019-09-03 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
introduction

@@
 \begin{abstract}
-    ABM is an effective tool for analysis of complex systems with long term emergent behavior.
-In this study we apply ABM to analyse the long term behavior of Keep’s random beacon.
-We look for the emergence of steady state behavior, at which point we evaluate the sensitivity of specific group and signature characteristics to various parameters.
-The results of this study illustrates the effectiveness of ABM as an aid to the design of novel distributed systems.
+    ABM is an effective tool for analysis of complex systems with long term 
+    emergent behavior. In this study we apply ABM to analyse the long term 
+    behavior of Keep’s random beacon. We look for the emergence of steady 
+    state behavior, at which point we evaluate the sensitivity of specific 
+    group and signature characteristics to various parameters. The results 
+    of this study illustrates the effectiveness of ABM as an aid to the design 
+    of novel distributed systems.
 
@@
 
-\section{Agent Based Modeling}
-
-Overview of Agent Based Modeling and methods
+\section{Agent Based Modeling (ABM)}
+ABM has traditionally been a tool to simulate complex dynamic systems 
+such as the spread of pathogens \cite{Bauer2009}, social psychology 
+\cite{Smith2007}, and financial markets \cite{Feng2012}. It is well suited
+to systems that resist simple analytical solutions due to the interaction of 
+complex individual agents with varying attributes. As a bottom up approach, ABM
+has been gaining in popularity over tradtional methods such as Discrete Event
+Simulation, and can provide more convincing theoretical analysis than approaches
+such as general equilibrium analysis \cite{Wang2018}.
 
@@
 
+\bibliographystyle{plain}
+\bibliography{Simulation_paper.bib}
 \end{document}

### 2019-09-06 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
checkpoint

@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Prashanth Irudayaraj}
+\author{\IEEEauthorblockN{Prashanth Irudayaraj}
 \IEEEauthorblockA{\textit{Keep Network} \\
@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Antonio Cordozo}
+\IEEEauthorblockN{Antonio Cordozo}
 \IEEEauthorblockA{\textit{Keep Network} \\
@@
 \and
-\IEEEauthorblockN{4\textsuperscript{th} Promethea Raschke}
+\IEEEauthorblockN{Promethea Raschke}
 \IEEEauthorblockA{\textit{Keep Network} \\
@@
 \and
-\IEEEauthorblockN{5\textsuperscript{th} Markus Fix}
+\IEEEauthorblockN{Markus Fix}
 \IEEEauthorblockA{\textit{Keep Network} \\
@@
 \and
-\IEEEauthorblockN{6\textsuperscript{th} Liam Zebedee}
+\IEEEauthorblockN{Liam Zebedee}
 \IEEEauthorblockA{\textit{Keep Network} \\
@@
 
+The nascent field of token engineering is currently establishing its own set 
+of tools and processes. As such, ABM lends itself well to analyzing these systems
+to support the design process and evaluate system state after launch.
+
 \section{Analysis of Token based systems}
@@
 \section{Overview of the Keep Random Beacon}
+The Keep Network random beacon uses a threshold relay simuliar to the one proposed
+by DFINITY and based on the BLS signature scheme \cite{} (NEED CITATION)
 
 \subsection{Role of the model in the design process}
+The initial architecture of the Keep beacon was designed by (need input from Antonio)
+what purpose did the simulation serve?
 
-\subsection{Key research questions}
+\section{Key research questions}
+\subsection{When could steady state behavior emerge?}
+Emergence of steady state behavior occurs as a confluence of several factors and is difficult
+to predict at the design stage. Specifically, process that take several blocks to complete 
+such as DKG that often occur asynchronously can create large swings in values such as number of active
+groups or percentage of compromised groups.
+
+\subsection{What are the effects of node failures on system behavior?}
+Nodes may go offline or fail entireley. Since their participation in groups is critical to the 
+success of the threshold relay, it is important to understand the impact of various levels
+of failure on group characteristics. In particular, failures can result in disproportionate ownership
+of groups which may cause a byzantine fault to occur.
+
+\subsection{What are the effects of stake distributions on system behavior?}
+Stake distributions can also skew ownership of groups and can lead to a byzantine fault. A more
+centralized distribution could once again lead to a greater ownership of groups by a few entities
+thus creating conditions for the group to be compromised.
 
@@
 
+\subsection{Model Structure}
+We construct the model using the MESA ABM framework (cite). MESA consists of an agent class with
+attributes and methods. We generate 3 types of agents Nodes, Groups, and Signatures. TABLE shows 
+the specific differences in each of these.
+
+ADD table for Agent types
+
+The simulation model consists of the model class which instantiates the various agents
+and steps through the simulation. At each step the state of the model and each agent
+is updated. The scheduler manages the sequence of state changes. For this model we use
+a simulataneous activation scheduler, which first stages updates for each agent and then 
+advances them simultaneously.  (NEED TO CHECK SCHEDULER SEQUENCE AGAIN)
+
 \subsection{Terminology}
+Node: A computational entity with memory and computational power sufficient to to run a 
+keep client
 
-\subsection{Structure of the Model}
+Node Owner: may own 1 or more nodes and can allocate different levels of stake to each node
+owned
+
+Stake: A bond that make a node eligible to participate in a group
+
+Group: A collection of nodes who have successfully completed DKG together
+
+DKG (Distributed Key Generation): The processes of generating keys for each node enabling
+them to sign using Keep's version of Threshold ECDSA \cite{Gennaro2018}.
+
+Signature: The process of securely generating a random number using Threshold ECDSA \cite{Gennaro2018}
+
+Ownership Percent: The level of ownership a specific entity has in a group or signature
+
+Lynchpin: A node who's ownership exceeds the maximum malicious threshold
+
+\subsection{Runs}
 \begin{itemize}

### 2019-09-09 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
stochastic assumptions

@@
 
+\subsection{Key Terms}
+\begin{itemize}
+\item Node: A computational entity with memory and computational power sufficient to to run a 
+keep client
+
+\item Node Owner: may own 1 or more nodes and can allocate different levels of stake to each node
+    owned
+
+\item Stake: A bond that make a node eligible to participate in a group
+
+\item Group: A collection of nodes who have successfully completed DKG together
+
+\item DKG (Distributed Key Generation): The processes of generating keys for each node enabling
+    them to sign using Keep's version of Threshold ECDSA \cite{Gennaro2018}.
+
+\item Signature: The process of securely generating a random number using Threshold ECDSA \cite{Gennaro2018}
+
+\item Ownership Percent: The level of ownership a specific entity has in a group or signature
+
+\item Lynchpin: A node who's ownership exceeds the maximum malicious threshold
+\end{itemize}
+
 \subsection{Model Structure}
@@
 
-\subsection{Terminology}
-Node: A computational entity with memory and computational power sufficient to to run a 
-keep client
-
-Node Owner: may own 1 or more nodes and can allocate different levels of stake to each node
-owned
-
-Stake: A bond that make a node eligible to participate in a group
-
-Group: A collection of nodes who have successfully completed DKG together
-
-DKG (Distributed Key Generation): The processes of generating keys for each node enabling
-them to sign using Keep's version of Threshold ECDSA \cite{Gennaro2018}.
-
-Signature: The process of securely generating a random number using Threshold ECDSA \cite{Gennaro2018}
-
-Ownership Percent: The level of ownership a specific entity has in a group or signature
-
-Lynchpin: A node who's ownership exceeds the maximum malicious threshold
+Usually steps measure a change in time. Therefore for our simulation we assume
+1 step = 1 block.
 
 \subsection{Runs}
+We perform two sets of experiments to answer our research questions. 
 \begin{itemize}
 
-\item Single run
-\item Multiple runs
+\item Single run: Our single run of 1000 steps provide a first look at the 
+performance of the sim, quickly. We also use this first experiment to evaluate
+when steady state behavior could occur. We also perform some initial evaluations
+of the impact of different stake distributions.
+
+\item Multiple runs: The second experiment consists of multiple runs with varying 
+parameters. For each change in parameter we perform 6 runs. By varying parameters 
+in these runs we attempt to identify sensitivity. We measure this sensitivity after
+the start of steady state behavior which we identify in the single run.
 
@@
 \subsection{Assumptions}
+
+\textit{Stochastic Assumptions}
+To simplify the model we make stochastic assumptions for exogenous processes.
+
 \begin{itemize}
-\item Stochastic Assumptions
-\item Ticket distribution Assumptions
-\item Model Assumptions
+
+\item Node Connection Delay: We apply a random uniform distribution to a user specified range (NEED JUSTIFICATION OR A JUSTIFIED SAMPLING)
+\item Node Connection Failure: This is one of the parameters we intend to adjust to test for sensitivity. Therefore we
+randomly pick a percentage of nodes to fail using a uniform distribution.
+\item Node Death: We uniform randomly pick nodes to die at a user specified rate.
+\item Signature Delay: A delay between when a signature is triggered and when it is executed. We use a poisson distribution. (NEED JUSTIFICATION or REFERENCE)
+\item Node Owner Assignment: We use a normal distribution to assign owners to nodes. (NEED JUSTIFICATION)
 \end{itemize}
+
+\textit{Ticket distribution} Assumptions
+Model Assumptions
 

### 2019-09-16 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
switching branch

@@
 \textit{Stochastic Assumptions}
+
 To simplify the model we make stochastic assumptions for exogenous processes.
@@
 
-\textit{Ticket distribution} Assumptions
+\textit{Stake distribution}
+
+Since one of our research questions involves understanding the effects of centralization
+on system behavior, we use three different token distribution models with 
+varying degrees of decentraliation to evaluate this impact.
+
+\begin{itemize}
+\item Linear Distribution: We assume a simple linear distribution as our most 
+decentralized case. We take 50000 stakes and allocate them linearly to 100 nodes
+as shown in Figure \ref{fig:linear_distribution}
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{linear.png}
+    \caption{Linear Stage Distribution}
+    \label{fig:linear_distribution}
+\end{figure}
+
+\item Ethereum Distribution: In the spectrum of decentralization, we assume 
+ETH to be moderateley decentralized. We therefore take the distribution of the 
+top 30 percent account holders and apply it with some normalization in Figure \ref{fig:eth_distribution}.
+(NEED TO JUSTIFY TOP 30 PERCENT)
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{eth_distribution.png}
+    \caption{Top 30 Percent Ethereum Distribution}
+    \label{fig:eth_distribution}
+\end{figure}
+
+\item Assumed Stake Distribution: Should we disclose?
+\end{itemize}
+
+Assumptions
 Model Assumptions
@@
 \section{Results}
+\subsection{Emergence of steady state behavior}
+Using the single run experiment, we discover that steady state behavior
+begins at around 400 blocks. This appears due to the smoothening out of bootstrapping
+effects. (NEED TO CHECK SIM AS STEADY STATE SEEMS TO BE IN FLUX)
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{steady_state.png}
+    \caption{Emergence of Steady State Behavior}
+    \label{fig:steady_state}
+\end{figure}
+
+\subsection{Convergence pressures}
+The model primarily converges to steady state due to factors such as
+signature request frequency, node availability, group creation/expiration
+
+\subsection{Effects of Node failures on group and signature characteristics}
+
 \begin{itemize}
-\item Emergence of steady state behavior
-\item Effects of Node failures on group and signature characteristics
     \item Effects of stake distributions on group and signature characteristics

### 2019-09-19 Mesa Simulations/agent.py
changing distr to apply to owner instead of node

@@ -9,7 +9,7 @@ class Node(Agent):
     the number of tokens owned by the node """
     def __init__(self, unique_id, node_id, model, tickets, 
     failure_percent, death_percent, node_connection_delay,
-    node_mainloop_connection_delay, misbehaving_nodes):
+    node_mainloop_connection_delay, misbehaving_nodes, owner):
         super().__init__(unique_id, model)
         self.id = unique_id
         self.type = "node"
@@ -18,7 +18,6 @@ class Node(Agent):
         self.ticket_list = []
         self.connection_status = "not connected" #change later to event - currently used for node failure process
         self.connection_delay = np.random.randint(0,node_connection_delay) #uniform randomly assigned connection delay step value
-        self.mainloop_fork_delay = np.random.randint(0,node_mainloop_connection_delay) #uniform randomly assigned connection delay step value
         self.timer = self.model.timer
         self.node_connection_failure_percent = failure_percent
         self.node_death_percent = death_percent
@@ -42,11 +41,9 @@ class Node(Agent):
             else:
                 self.connection_status = "connected"
                 self.model.active_nodes[self.id] = self # add to the active nodes list
-                
 
     def advance(self):
         pass
-
 
     def generate_tickets(self):
         #generates tickets using the uniform distribution
@@ -98,6 +95,7 @@ class Group(Agent):
                 self.model.active_groups[self.id] = self # add to active groups list
         elif self.status == "active":
             """ At each step check if the group has expired """
+            self.calculate_malicious_percent #calculate the current malicious percent
             self.expiry -=1
             if self.expiry <= 0: 
                 self.status = "expired"
@@ -119,6 +117,13 @@ class Group(Agent):
         self.malicious_percent = temp_malicious_count/sum(temp_distr)
         self.ownership_distr = temp_distr
 
+    def calculate_malicious_percent(self):
+        temp_malicious_count = 0
+        for node in self.members:    
+            if node.malicious:
+                temp_malicious_count +=1
+        self.malicious_percent = temp_malicious_count/sum(self.ownership_distr)
+
 
     def calculate_offline(self):
         offline_count = 0
@@ -126,8 +131,7 @@ class Group(Agent):
             if node.connection_status == "not connected": 
                 offline_count +=1
         return offline_count
-
-    
+   
 
 class Signature(Agent):
     def __init__(self, unique_id, model, group_object):

### 2019-09-19 Mesa Simulations/model.py

@@ -44,8 +44,7 @@ class Beacon_Model(Model):
         self.total_signatures = 0
         self.failed_signature_threshold = failed_signature_threshold
         self.perc_failed_signatures = 0
-        self.node_ownership_params = node_ownership_params
-        self.owner_buckets = {i : np.random.randint(100)<30 for i in range(20)} 
+        self.number_of_owners = len(ticket_distribution)
         self.datacollector = DataCollector(
             model_reporters = {"# of Active Groups":"num_active_groups",
              "# of Active Nodes":"num_active_nodes",
@@ -71,14 +70,21 @@ class Beacon_Model(Model):
         #create log file
         log.basicConfig(filename=log_filename + str(run_number), filemode='w', format='%(name)s - %(levelname)s - %(message)s')
         self.log = log
+
         print("creating nodes")
         #create nodes
-        for i in range(nodes):
+        for i in range(self.number_of_owners):
+            owner_total_stake = self.ticket_distribution[i]
+
+
             node = agent.Node(i, i, self, 
             self.ticket_distribution[i], 
             node_failure_percent, 
             node_death_percent, 
-            node_connection_delay, node_mainloop_connection_delay, misbehaving_nodes)
+            node_connection_delay, 
+            node_mainloop_connection_delay, 
+            misbehaving_nodes,
+            )
             self.newest_id = i
             self.schedule.add(node)
         self.newest_id +=1
@@ -197,8 +203,7 @@ class Beacon_Model(Model):
             if group.type == "group":
                 total_groups +=1
                 malicious_array.append(group.malicious_percent) #creates an array of malicious percents for each group
-        
-
+        print(malicious_array)
         self.median_malicious_group_percents = np.median(malicious_array)
         self.perc_compromised_groups = sum(np.array(malicious_array)>=self.compromised_threshold)/(total_groups+0.000000000000000001)
 

### 2019-09-24 Mesa Simulations/agent.py
resolved issues with variable number of nodes

@@ -7,13 +7,12 @@ class Node(Agent):
     """ Node: One hardware device used to stake tokens on the network. 
     Each node will create virtual stakers proportional to
     the number of tokens owned by the node """
-    def __init__(self, unique_id, node_id, model, tickets, 
+    def __init__(self, unique_id, model, tickets, 
     failure_percent, death_percent, node_connection_delay,
-    node_mainloop_connection_delay, misbehaving_nodes, owner):
+    node_mainloop_connection_delay, owner, malicious):
         super().__init__(unique_id, model)
         self.id = unique_id
         self.type = "node"
-        self.node_id = node_id
         self.num_tickets = int(tickets)
         self.ticket_list = []
         self.connection_status = "not connected" #change later to event - currently used for node failure process
@@ -24,8 +23,9 @@ class Node(Agent):
         self.connection_failure = False
         self.death = False
         self.dkg_misbehaving = False
-        self.node_owner = int((np.random.normal(self.model.node_ownership_params[0], self.model.node_ownership_params[1])+3.5)*15) # picks an owner using the normal distribution and parameters set in the sim
-        self.malicious = self.model.owner_buckets[math.ceil(self.node_owner/10)] # sets the node as malicious if its owner is malicious
+        self.node_owner = owner
+        self.malicious = malicious
+        self.model.newest_id +=1 # increments the model agent ID
 
     def step(self):
         #simulate node failure
@@ -78,6 +78,7 @@ class Group(Agent):
         self.process_complete = False
         self.dkg_block_delay = self.model.dkg_block_delay
 
+        self.model.newest_id +=1 # increments the model agent ID by 1 after a new node is created 
         self.calculate_ownership_distr()
 
 
@@ -111,7 +112,7 @@ class Group(Agent):
         temp_distr = np.zeros(self.model.num_nodes)
         temp_malicious_count = 0
         for node in self.members:    
-            temp_distr[node.node_id] +=1 # increments by 1 for each node index everytime it exists in the member list, at each step
+            temp_distr[node.id] +=1 # increments by 1 for each node index everytime it exists in the member list, at each step
             if node.malicious:
                 temp_malicious_count +=1
         self.malicious_percent = temp_malicious_count/sum(temp_distr)
@@ -142,12 +143,13 @@ class Signature(Agent):
         self.status = "started"
         self.delay = np.random.poisson(self.model.signature_delay) #delay between when it is triggered and when it hits the chain
         self.ownership_distr = []
[…]

### 2019-09-24 Mesa Simulations/model.py

@@ -7,6 +7,7 @@ import logging as log
 import numpy as np
 import random as rnd
 import time
+import math
 
 class Beacon_Model(Model):
     """The model"""
@@ -15,8 +16,8 @@ class Beacon_Model(Model):
     node_failure_percent, node_death_percent,
     signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
     log_filename, run_number, dkg_block_delay, compromised_threshold,
-    failed_signature_threshold, node_ownership_params, min_stake_amount, owner_mode):
-        self.num_nodes = nodes
+    failed_signature_threshold, min_stake_amount, owner_mode, malicious_owners_percent):
+        self.num_nodes = 0
         self.schedule = SimultaneousActivation(self)
         self.relay_request = False
         self.active_groups = {}
@@ -73,20 +74,25 @@ class Beacon_Model(Model):
 
         print("creating nodes")
         #create nodes
-        if owner_mode = 1: # owners nodes are proportional to its total stake amt
+        if owner_mode == 1: # owners nodes are proportional to its total stake amt
             for i in range(self.number_of_owners): 
                 total_owner_nodes = math.floor(self.ticket_distribution[i]/self.min_stake_amount)
                 tickets = min_stake_amount
-                    for j in range(total_owner_nodes)
+                for j in range(total_owner_nodes):
+                    malicious = np.random.randint(0,100)<30
+                    print('creating node')
                     node = agent.Node(self.newest_id, self, 
                     tickets, 
                     node_failure_percent, 
                     node_death_percent, 
                     node_connection_delay, 
-                    node_mainloop_connection_delay
+                    node_mainloop_connection_delay,
+                    i,
+                    malicious
                     )
                     self.schedule.add(node)
-        elif owner_mode = 2: # 1 node per owner
+                    self.num_nodes+=1
+        elif owner_mode == 2: # 1 node per owner
             for i in range(self.number_of_owners): 
                 tickets = self.ticket_distribution[i]
                 node = agent.Node(self.newest_id, self, 
@@ -94,9 +100,11 @@ class Beacon_Model(Model):
                 node_failure_percent, 
                 node_death_percent, 
                 node_connection_delay, 
-                node_mainloop_connection_delay
+                node_mainloop_connection_delay,
+                owner
                 )
                 self.schedule.add(node)
+                self.num_nodes+=1
 
 
 
@@ -167,7 +175,7 @@ class Beacon_Model(Model):
 
             # add create the list of member nodes
[…]

### 2019-09-24 Mesa Simulations/model.py
changed owner_mode to self_operator mode

@@ -11,12 +11,12 @@ import math
 
 class Beacon_Model(Model):
     """The model"""
-    def __init__(self, nodes, ticket_distribution, active_group_threshold, 
+    def __init__(self, ticket_distribution, active_group_threshold, 
     group_size, max_malicious_threshold_percent, group_expiry, 
     node_failure_percent, node_death_percent,
     signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
     log_filename, run_number, dkg_block_delay, compromised_threshold,
-    failed_signature_threshold, min_stake_amount, owner_mode, malicious_owners_percent):
+    failed_signature_threshold, min_stake_amount, self_operator_mode, malicious_owners_percent):
         self.num_nodes = 0
         self.schedule = SimultaneousActivation(self)
         self.relay_request = False
@@ -211,7 +211,6 @@ class Beacon_Model(Model):
                     temp_inactive_node_list[agent.id] = agent
         self.active_nodes = temp_active_node_list
         self.inactive_nodes = temp_inactive_node_list
-        print(self.active_nodes)
 
     def calculate_compromised_groups(self):
     #Calculate compromised groups
@@ -221,7 +220,6 @@ class Beacon_Model(Model):
             if group.type == "group":
                 total_groups +=1
                 malicious_array.append(group.malicious_percent) #creates an array of malicious percents for each group
-        print(malicious_array)
         self.median_malicious_group_percents = np.median(malicious_array)
         self.perc_compromised_groups = sum(np.array(malicious_array)>=self.compromised_threshold)/(total_groups+0.000000000000000001)
 

### 2019-09-24 Mesa Simulations/agent.py
changed owner to operator in node agent

@@ -9,7 +9,7 @@ class Node(Agent):
     the number of tokens owned by the node """
     def __init__(self, unique_id, model, tickets, 
     failure_percent, death_percent, node_connection_delay,
-    node_mainloop_connection_delay, owner, malicious):
+    node_mainloop_connection_delay, operator, malicious):
         super().__init__(unique_id, model)
         self.id = unique_id
         self.type = "node"
@@ -23,7 +23,7 @@ class Node(Agent):
         self.connection_failure = False
         self.death = False
         self.dkg_misbehaving = False
-        self.node_owner = owner
+        self.node_operator = operator
         self.malicious = malicious
         self.model.newest_id +=1 # increments the model agent ID
 

### 2019-09-24 Mesa Simulations/model.py
changed malicious_owner_percent to operator

@@ -16,7 +16,7 @@ class Beacon_Model(Model):
     node_failure_percent, node_death_percent,
     signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
     log_filename, run_number, dkg_block_delay, compromised_threshold,
-    failed_signature_threshold, min_stake_amount, self_operator_mode, malicious_owners_percent):
+    failed_signature_threshold, min_stake_amount, self_operator_mode, malicious_operator_percent):
         self.num_nodes = 0
         self.schedule = SimultaneousActivation(self)
         self.relay_request = False

### 2019-09-24 Mesa Simulations/agent.py
changed Group agent to Signing_Group

@@ -59,7 +59,7 @@ class Node(Agent):
         if self.death == False: # does not reset the failure trigger if the death trigger is true
             self.failure = False
 
-class Group(Agent):
+class Signing_Group(Agent):
     """ A Group """
     def __init__(self, unique_id, model, members, expiry):
         super().__init__(unique_id, model)

### 2019-09-24 Mesa Simulations/model.py

@@ -178,7 +178,7 @@ class Beacon_Model(Model):
                 group_members.append(self.active_nodes[node_id[1]]) # pick the node with the given ID from the active nodes list
             
             #create a group agent which can track expiry, sign, etc
-            group_object = agent.Group(self.newest_id, self, group_members, self.group_expiry)
+            group_object = agent.Signing_Group(self.newest_id, self, group_members, self.group_expiry)
 
 
             #add group to schedule

### 2019-09-24 Mesa Simulations/model.py
changed ticket_distribution to stake_distribution

@@ -11,7 +11,7 @@ import math
 
 class Beacon_Model(Model):
     """The model"""
-    def __init__(self, ticket_distribution, active_group_threshold, 
+    def __init__(self, stake_distribution, active_group_threshold, 
     group_size, max_malicious_threshold_percent, group_expiry, 
     node_failure_percent, node_death_percent,
     signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
@@ -28,7 +28,7 @@ class Beacon_Model(Model):
         self.active_group_threshold = active_group_threshold # number of groups that will always be maintained in an active state
         self.max_malicious_threshold_percent = max_malicious_threshold_percent # threshold above which a signature is deemed to be compromised, typically 51%
         self.group_size = group_size
-        self.ticket_distribution = ticket_distribution
+        self.stake_distribution = stake_distribution
         self.newest_id = 0 #ID count for agents
         self.group_expiry = group_expiry
         self.bootstrap_complete = False # indicates when the initial active group list bootstrap is complete
@@ -45,7 +45,7 @@ class Beacon_Model(Model):
         self.total_signatures = 0
         self.failed_signature_threshold = failed_signature_threshold
         self.perc_failed_signatures = 0
-        self.number_of_owners = len(ticket_distribution)
+        self.number_of_owners = len(stake_distribution)
         self.min_stake_amount = min_stake_amount
         self.datacollector = DataCollector(
             model_reporters = {"# of Active Groups":"num_active_groups",
@@ -76,7 +76,7 @@ class Beacon_Model(Model):
         #create nodes
         if owner_mode == 1: # owners nodes are proportional to its total stake amt
             for i in range(self.number_of_owners): 
-                total_owner_nodes = math.floor(self.ticket_distribution[i]/self.min_stake_amount)
+                total_owner_nodes = math.floor(self.stake_distribution[i]/self.min_stake_amount)
                 tickets = min_stake_amount
                 for j in range(total_owner_nodes):
                     malicious = np.random.randint(0,100)<30
@@ -94,7 +94,7 @@ class Beacon_Model(Model):
                     self.num_nodes+=1
         elif owner_mode == 2: # 1 node per owner
             for i in range(self.number_of_owners): 
-                tickets = self.ticket_distribution[i]
+                tickets = self.stake_distribution[i]
                 node = agent.Node(self.newest_id, self, 
                 tickets, 
                 node_failure_percent, 

### 2019-09-24 Mesa Simulations/model.py
changed self_operator to just operator

@@ -16,7 +16,7 @@ class Beacon_Model(Model):
     node_failure_percent, node_death_percent,
     signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
     log_filename, run_number, dkg_block_delay, compromised_threshold,
-    failed_signature_threshold, min_stake_amount, self_operator_mode, malicious_operator_percent):
+    failed_signature_threshold, min_stake_amount, operator_mode, malicious_operator_percent):
         self.num_nodes = 0
         self.schedule = SimultaneousActivation(self)
         self.relay_request = False
@@ -74,7 +74,7 @@ class Beacon_Model(Model):
 
         print("creating nodes")
         #create nodes
-        if owner_mode == 1: # owners nodes are proportional to its total stake amt
+        if operator_mode == 1: # owners nodes are proportional to its total stake amt
             for i in range(self.number_of_owners): 
                 total_owner_nodes = math.floor(self.stake_distribution[i]/self.min_stake_amount)
                 tickets = min_stake_amount
@@ -87,13 +87,14 @@ class Beacon_Model(Model):
                     node_death_percent, 
                     node_connection_delay, 
                     node_mainloop_connection_delay,
-                    i,
+                    i,# operator
                     malicious
                     )
                     self.schedule.add(node)
                     self.num_nodes+=1
-        elif owner_mode == 2: # 1 node per owner
-            for i in range(self.number_of_owners): 
+        elif operator_mode == 2: # 1 node per owner
+            for i in range(self.number_of_owners):
+                malicious = np.random.randint(0,100)<30 
                 tickets = self.stake_distribution[i]
                 node = agent.Node(self.newest_id, self, 
                 tickets, 
@@ -101,7 +102,8 @@ class Beacon_Model(Model):
                 node_death_percent, 
                 node_connection_delay, 
                 node_mainloop_connection_delay,
-                owner
+                i,# operator
+                malicious
                 )
                 self.schedule.add(node)
                 self.num_nodes+=1

### 2019-09-25 Mesa Simulations/model.py
fixed node operator mis label error

@@ -66,7 +66,7 @@ class Beacon_Model(Model):
             "Malicious %" : lambda x : x.malicious_percent if x.type == "group" else None,
             "Offline %" : lambda x : x.offline_percent if x.type == "group" or x.type == "signature" else None,
             "Dominator %": lambda x : x.dominator_percent if x.type == "signature" else None,
-            "Owner": lambda x : x.node_owner if x.type == "node" else None})
+            "Owner": lambda x : x.node_operator if x.type == "node" else None})
 
         #create log file
         log.basicConfig(filename=log_filename + str(run_number), filemode='w', format='%(name)s - %(levelname)s - %(message)s')

### 2019-09-25 Mesa Simulations/agent.py
replaced dominator with lynchpin

@@ -145,7 +145,7 @@ class Signature(Agent):
         self.ownership_distr = []
         self.signature_process_complete = False
         self.block_delay_complete = False
-        self.dominator_percent = 0
+        self.lynchpin_percent = 0
         self.offline_percent = 0
         self.owner_lynchpin_percent = 0
 
@@ -177,7 +177,7 @@ class Signature(Agent):
         self.ownership_distr = temp_signature_distr
         failed_list = np.array(self.group.ownership_distr)-np.array(self.ownership_distr)
         self.offline_percent = sum(failed_list)/sum(self.group.ownership_distr)
-        self.dominator_percent = (sum(failed_list) + max(self.ownership_distr))/sum(self.group.ownership_distr) # adds the failed node virtual stakers and max node virtual stakers
+        self.lynchpin_percent = (sum(failed_list) + max(self.ownership_distr))/sum(self.group.ownership_distr) # adds the failed node virtual stakers and max node virtual stakers
         
         #Calculate lynchpin owner
         shares_by_staker = {}

### 2019-09-25 Mesa Simulations/model.py

@@ -65,7 +65,7 @@ class Beacon_Model(Model):
             "Ownership Distribution" : lambda x : x.ownership_distr if x.type =="group" or x.type == "signature" else None,
             "Malicious %" : lambda x : x.malicious_percent if x.type == "group" else None,
             "Offline %" : lambda x : x.offline_percent if x.type == "group" or x.type == "signature" else None,
-            "Dominator %": lambda x : x.dominator_percent if x.type == "signature" else None,
+            "Dominator %": lambda x : x.lynchpin_percent if x.type == "signature" else None,
             "Owner": lambda x : x.node_operator if x.type == "node" else None})
 
         #create log file
@@ -146,7 +146,7 @@ class Beacon_Model(Model):
 
         #calculate model measurements
         self.calculate_compromised_groups()
-        self.calculate_dominated_signatures()
+        self.calculate_lynchpinned_signatures()
         
         #advance the agents
         self.schedule.step()
@@ -225,21 +225,21 @@ class Beacon_Model(Model):
         self.median_malicious_group_percents = np.median(malicious_array)
         self.perc_compromised_groups = sum(np.array(malicious_array)>=self.compromised_threshold)/(total_groups+0.000000000000000001)
 
-    def calculate_dominated_signatures(self):
-        dominator_array = []
-        dominator_count = 0
+    def calculate_lynchpinned_signatures(self):
+        lynchpin_array = []
+        lynchpin_count = 0
         total_signatures = 0
         failed_signatures = 0
         for signature in self.schedule.agents:
             if signature.type == "signature":
                 total_signatures +=1
-                dominator_array.append(signature.dominator_percent)
-                dominator_count += (signature.dominator_percent>=self.max_malicious_threshold_percent)
+                lynchpin_array.append(signature.lynchpin_percent)
+                lynchpin_count += (signature.lynchpin_percent>=self.max_malicious_threshold_percent)
                 failed_signatures += (signature.offline_percent>=self.failed_signature_threshold)
 
         self.perc_failed_signatures = failed_signatures/(total_signatures+0.00000000000000001)
-        self.median_dominated_signatures_percents = np.median(dominator_array)
-        self.perc_dominated_signatures = dominator_count/(total_signatures+0.00000000000000001)
+        self.median_dominated_signatures_percents = np.median(lynchpin_array)
+        self.perc_dominated_signatures = lynchpin_count/(total_signatures+0.00000000000000001)
         self.total_signatures = total_signatures
 
 

### 2019-09-25 Mesa Simulations/agent.py
changed dominator to lynchpin

@@ -187,7 +187,7 @@ class Signature(Agent):
                 try:
                     shares_by_staker[self.model.active_nodes[node_id].node_owner]+=node_tickets #add tickets to owner shares
                 except:
-                    shares_by_staker.update({self.model.active_nodes[node_id].node_owner : node_tickets})
+                    shares_by_staker.update({self.model.active_nodes[node_id].node_operator : node_tickets})
                     
         self.owner_lynchpin_percent = shares_by_staker[max(shares_by_staker)]/total_tickets
 

### 2019-09-25 Mesa Simulations/model.py

@@ -53,8 +53,8 @@ class Beacon_Model(Model):
              "# of Signatures":"total_signatures",
              "Median Malicious Group %": "median_malicious_group_percents",
              "% Compromised Groups": "perc_compromised_groups",
-             "Median Dominator %":"median_dominated_signatures_percents",
-             "% Dominated signatures":"perc_dominated_signatures",
+             "Median Lynchpin %":"median_dominated_signatures_percents",
+             "% Lynchpinned signatures":"perc_dominated_signatures",
              "Failed Singature %" : "perc_failed_signatures" },
             agent_reporters={"ID": "id" , 
             "Type" : "type",
@@ -65,7 +65,7 @@ class Beacon_Model(Model):
             "Ownership Distribution" : lambda x : x.ownership_distr if x.type =="group" or x.type == "signature" else None,
             "Malicious %" : lambda x : x.malicious_percent if x.type == "group" else None,
             "Offline %" : lambda x : x.offline_percent if x.type == "group" or x.type == "signature" else None,
-            "Dominator %": lambda x : x.lynchpin_percent if x.type == "signature" else None,
+            "Lynchpin %": lambda x : x.lynchpin_percent if x.type == "signature" else None,
             "Owner": lambda x : x.node_operator if x.type == "node" else None})
 
         #create log file
@@ -80,7 +80,6 @@ class Beacon_Model(Model):
                 tickets = min_stake_amount
                 for j in range(total_owner_nodes):
                     malicious = np.random.randint(0,100)<30
-                    print('creating node')
                     node = agent.Node(self.newest_id, self, 
                     tickets, 
                     node_failure_percent, 

### 2019-09-27 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added steady state behavior figure
explained steady state behavior

@@
 \usepackage{xcolor}
+\usepackage{multicol}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \subsection{Emergence of steady state behavior}
-Using the single run experiment, we discover that steady state behavior
-begins at around 400 blocks. This appears due to the smoothening out of bootstrapping
-effects. (NEED TO CHECK SIM AS STEADY STATE SEEMS TO BE IN FLUX)
+Using the single run experiment, we discover that system stabalizes to steady state
+usually around 400 blocks, usually due to normalization of bootstrapping states. 
+However, final steady state values for the percentage of total groups that are compromised
+appears to vary significantly and is dependent on the degree of concentration in the 
+stake distribution.
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{steady_state.png}
-    \caption{Emergence of Steady State Behavior}
-    \label{fig:steady_state}
-\end{figure}
+For concentrated distributions such as Ethereum, the steady state level of compromised
+groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
+to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
+distribution, we see steady steat levels within the 60-80 percent band for the given set
+of parameters (NOTE PARAMETER SETTINGS). \ref{fig:steady_state}
 
@@
 
+\newpage
+
+\begin{figure*}[h]
+    \onecolumn
+    \centering
+    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
+    \caption{Emergence of Steady State Behavior}
+    \label{fig:steady_state}
+\end{figure*}
+
+\newpage
 \bibliographystyle{plain}

### 2019-09-27 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
steady state active group count

@@
 distribution, we see steady steat levels within the 60-80 percent band for the given set
-of parameters (NOTE PARAMETER SETTINGS). \ref{fig:steady_state}
+of parameters (NOTE PARAMETER SETTINGS) \ref{fig:steady_state}. We expect a similar band but at
+different parameter levels for different parameter settings.
 
 \subsection{Convergence pressures}
+
 The model primarily converges to steady state due to factors such as
-signature request frequency, node availability, group creation/expiration
+signature request frequency, node availability, group creation/expiration, and....
+
+\textit{ Steady state active group count:} Groups are generated with every request, and intially
+during the bootstrap phase a set number of groups are generated with available nodes. In the current
+simulation, requests are generated as coin toss at each step. The steady state number of active groups
+is a function of number of new requests and rate of group expiry. Initially we
 

### 2019-09-30 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
moved figure of steady state results

@@
 The model primarily converges to steady state due to factors such as
-signature request frequency, node availability, group creation/expiration, and....
+signature request frequency, node availability, and group creation/expiration. We discuss a few
+steady state values of interest.
 
-\textit{ Steady state active group count:} Groups are generated with every request, and intially
+\textit{Active group count} Groups are generated with every request, and intially
 during the bootstrap phase a set number of groups are generated with available nodes. In the current
-simulation, requests are generated as coin toss at each step. The steady state number of active groups
-is a function of number of new requests and rate of group expiry. Initially we
+simulation, requests are generated as coin tosses (binomial) at each step. The steady state number of 
+active groups is a function of number of new requests and rate of group expiry. In the current setup, 
+we see the number of active groups converging to 15 after 400 blocks.
 
@@
 
-\newpage
+\bibliographystyle{plain}
+\bibliography{Simulation_paper.bib}
 
@@
     \label{fig:steady_state}
+    \multicolumn
 \end{figure*}
 
-\newpage
-\bibliographystyle{plain}
-\bibliography{Simulation_paper.bib}
 \end{document}

### 2019-09-30 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
started percent compromised groups percent

@@
 to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
-distribution, we see steady steat levels within the 60-80 percent band for the given set
+distribution, we see steady steat levels within the 50-80 percent band for the given set
 of parameters (NOTE PARAMETER SETTINGS) \ref{fig:steady_state}. We expect a similar band but at
@@
 we see the number of active groups converging to 15 after 400 blocks.
+
+\textit{Percent Compromised Groups} Steady state level of percent compromised
+groups appears to
 

### 2019-09-30 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/agent.py
added simulation files to conference paper branch

@@ -1,0 +1,195 @@
+from mesa import Agent, Model
+from mesa.time import RandomActivation
+import numpy as np
+import math
+
+class Node(Agent):
+    """ Node: One hardware device used to stake tokens on the network. 
+    Each node will create virtual stakers proportional to
+    the number of tokens owned by the node """
+    def __init__(self, unique_id, node_id, model, tickets, 
+    failure_percent, death_percent, node_connection_delay,
+    node_mainloop_connection_delay, misbehaving_nodes):
+        super().__init__(unique_id, model)
+        self.id = unique_id
+        self.type = "node"
+        self.node_id = node_id
+        self.num_tickets = int(tickets)
+        self.ticket_list = []
+        self.connection_status = "not connected" #change later to event - currently used for node failure process
+        self.connection_delay = np.random.randint(0,node_connection_delay) #uniform randomly assigned connection delay step value
+        self.mainloop_fork_delay = np.random.randint(0,node_mainloop_connection_delay) #uniform randomly assigned connection delay step value
+        self.timer = self.model.timer
+        self.node_connection_failure_percent = failure_percent
+        self.node_death_percent = death_percent
+        self.connection_failure = False
+        self.death = False
+        self.dkg_misbehaving = False
+        self.node_owner = int((np.random.normal(self.model.node_ownership_params[0], self.model.node_ownership_params[1])+3.5)*15) # picks an owner using the normal distribution and parameters set in the sim
+        self.malicious = self.model.owner_buckets[math.ceil(self.node_owner/10)] # sets the node as malicious if its owner is malicious
+
+    def step(self):
+        #simulate node failure
+        self.connection_failure = np.random.randint(0,100) < self.node_connection_failure_percent
+        self.death = np.random.randint (0,100) < self.node_death_percent
+
+        #disconnect the node if failure occurs
+        if (self.connection_failure or self.death) and self.connection_status == "connected":
+            self.node_disconnect()
+        else:
+            if self.connection_delay>0:
+                self.connection_delay -=1
+            else:
+                self.connection_status = "connected"
+                self.model.active_nodes[self.id] = self # add to the active nodes list
+                
+
+    def advance(self):
+        pass
+
+
+    def generate_tickets(self):
+        #generates tickets using the uniform distribution
+        self.ticket_list = np.random.random_sample(self.num_tickets)
+        
+    def node_disconnect(self):
[…]

### 2019-09-30 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/model.py

@@ -1,0 +1,260 @@
+from mesa import Model
+from mesa.time import SimultaneousActivation
+import agent
+import numpy as np
+from mesa.datacollection import DataCollector
+import logging as log
+import numpy as np
+import random as rnd
+import time
+
+class Beacon_Model(Model):
+    """The model"""
+    def __init__(self, nodes, ticket_distribution, active_group_threshold, 
+    group_size, max_malicious_threshold_percent, group_expiry, 
+    node_failure_percent, node_death_percent,
+    signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
+    log_filename, run_number, misbehaving_nodes, dkg_block_delay, compromised_threshold,
+    failed_signature_threshold, node_ownership_params):
+        self.num_nodes = nodes
+        self.schedule = SimultaneousActivation(self)
+        self.relay_request = False
+        self.active_groups = {}
+        self.num_active_groups = 0
+        self.active_nodes = {}
+        self.num_active_nodes = 0
+        self.inactive_nodes = []
+        self.active_group_threshold = active_group_threshold # number of groups that will always be maintained in an active state
+        self.max_malicious_threshold_percent = max_malicious_threshold_percent # threshold above which a signature is deemed to be compromised, typically 51%
+        self.group_size = group_size
+        self.ticket_distribution = ticket_distribution
+        self.newest_id = 0
+        self.group_expiry = group_expiry
+        self.bootstrap_complete = False # indicates when the initial active group list bootstrap is complete
+        self.group_formation_threshold = min_nodes # min nodes required to form a group
+        self.timer = 0
+        self.unsuccessful_signature_events = []
+        self.signature_delay = signature_delay
+        self.dkg_block_delay = dkg_block_delay
+        self.compromised_threshold = compromised_threshold
+        self.median_malicious_group_percents = 0
+        self.median_dominated_signatures_percents = 0
+        self.perc_dominated_signatures = 0
+        self.perc_compromised_groups = 0
+        self.total_signatures = 0
+        self.failed_signature_threshold = failed_signature_threshold
+        self.perc_failed_signatures = 0
+        self.node_ownership_params = node_ownership_params
+        self.owner_buckets = {i : np.random.randint(100)<30 for i in range(20)} 
+        self.datacollector = DataCollector(
+            model_reporters = {"# of Active Groups":"num_active_groups",
+             "# of Active Nodes":"num_active_nodes",
[…]

### 2019-09-30 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
fixed error in fig block

--- 2019-09-27 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
@@
 \usepackage{xcolor}
-\usepackage{multicol}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \subsection{Emergence of steady state behavior}
-Using the single run experiment, we discover that system stabalizes to steady state
-usually around 400 blocks, usually due to normalization of bootstrapping states. 
-However, final steady state values for the percentage of total groups that are compromised
-appears to vary significantly and is dependent on the degree of concentration in the 
-stake distribution.
+Using the single run experiment, we discover that steady state behavior
+begins at around 400 blocks. This appears due to the smoothening out of bootstrapping
+effects. (NEED TO CHECK SIM AS STEADY STATE SEEMS TO BE IN FLUX)
 
-For concentrated distributions such as Ethereum, the steady state level of compromised
-groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
-to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
-distribution, we see steady steat levels within the 60-80 percent band for the given set
-of parameters (NOTE PARAMETER SETTINGS) \ref{fig:steady_state}. We expect a similar band but at
-different parameter levels for different parameter settings.
-
-\subsection{Convergence pressures}
-
-The model primarily converges to steady state due to factors such as
-signature request frequency, node availability, group creation/expiration, and....
-
-\textit{ Steady state active group count:} Groups are generated with every request, and intially
-during the bootstrap phase a set number of groups are generated with available nodes. In the current
-simulation, requests are generated as coin toss at each step. The steady state number of active groups
-is a function of number of new requests and rate of group expiry. Initially we
+\begin{figure}
+    \includegraphics[width=\linewidth]{steady_state.png}
+    \caption{Emergence of Steady State Behavior}
+    \label{fig:steady_state}
+\end{figure}
 
@@
 
-\newpage
-
-\begin{figure*}[h]
-    \onecolumn
-    \centering
-    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
-    \caption{Emergence of Steady State Behavior}
-    \label{fig:steady_state}
-\end{figure*}
-
-\newpage
 \bibliographystyle{plain}

### 2019-10-03 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
adding agent table

--- 2019-09-30 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
@@
 
+Agent based systems could help evaluate trends in behavior related to
+various system parameters. They may not however, accurateley represent 
+actual system performance.
+
+Discuss levels of complexity, with citations. Why greater complexity may
+not get you much more insight.
+
 \section{Overview of the Keep Random Beacon}
@@
 
-\subsection{What are the effects of node failures on system behavior?}
+\subsection{How could node failures affect system behavior?}
 Nodes may go offline or fail entireley. Since their participation in groups is critical to the 
@@
 
-\subsection{What are the effects of stake distributions on system behavior?}
+\subsection{How could different stake distributions affect system behavior?}
 Stake distributions can also skew ownership of groups and can lead to a byzantine fault. A more
@@
 ADD table for Agent types
+\begin{table}[htbp]
+    \caption{Agent Types}
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    \textbf{Parameters}&\multicolumn{3}{|c|}{\textbf{Agents}} \\
+    \cline{2-4} 
+    \textbf{ } & \textbf{\textit{Node}}& \textbf{\textit{Group}}& \textbf{\textit{Signature}} \\
+    \hline
+    Unique ID & X & X & X \\
+    \hline
+    \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+    \end{tabular}
+    \label{table}
+    \end{center}
+    \end{table}
+
+Decide whether all parameters should be listed?
 
@@
 \subsection{Emergence of steady state behavior}
-Using the single run experiment, we discover that system stabalizes to steady state
-usually around 400 blocks, usually due to normalization of bootstrapping states. 
+Using the single run experiment, we discover that system consistently appears to 
+stabalizes to steady state usually around 400 blocks, and usually due to normalization of bootstrapping states. 
 However, final steady state values for the percentage of total groups that are compromised
@@
 stake distribution.
-
-For concentrated distributions such as Ethereum, the steady state level of compromised
-groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
-to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
-distribution, we see steady steat levels within the 50-80 percent band for the given set
-of parameters (NOTE PARAMETER SETTINGS) \ref{fig:steady_state}. We expect a similar band but at
-different parameter levels for different parameter settings.
 
@@
 
-\textit{Percent Compromised Groups} Steady state level of percent compromised
-groups appears to
+\textit{Percent Compromised Groups} For concentrated distributions such as Ethereum, the steady state level of compromised
+groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
+to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
+distribution, we see steady steat levels within the 50-80 percent band for the given set
+of parameters (NOTE PARAMETER SETTINGS) \ref{fig:steady_state}. We expect a similar band but at
+different parameter levels for different parameter settings. (CHECK THIS AGAIN)
+
+\textit{Percent Lynchpinned Signatures}
 
 \subsection{Effects of Node failures on group and signature characteristics}
+To evaluate the possible effects of node failure on group and signature characteristics, we use the
+multi-run study. We then observe trends in the specific parameters discussed below.
 
-\begin{itemize}
-    \item Effects of stake distributions on group and signature characteristics
-    \item Additional analyses?
-\end{itemize}
+\subsection{Effects of stake distributions on group and signature characteristics}
 
@@
     \label{fig:steady_state}
-    \multicolumn
 \end{figure*}

### 2019-10-03 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/agent.py

@@ -1,195 +1,0 @@
-from mesa import Agent, Model
-from mesa.time import RandomActivation
-import numpy as np
-import math
-
-class Node(Agent):
-    """ Node: One hardware device used to stake tokens on the network. 
-    Each node will create virtual stakers proportional to
-    the number of tokens owned by the node """
-    def __init__(self, unique_id, node_id, model, tickets, 
-    failure_percent, death_percent, node_connection_delay,
-    node_mainloop_connection_delay, misbehaving_nodes):
-        super().__init__(unique_id, model)
-        self.id = unique_id
-        self.type = "node"
-        self.node_id = node_id
-        self.num_tickets = int(tickets)
-        self.ticket_list = []
-        self.connection_status = "not connected" #change later to event - currently used for node failure process
-        self.connection_delay = np.random.randint(0,node_connection_delay) #uniform randomly assigned connection delay step value
-        self.mainloop_fork_delay = np.random.randint(0,node_mainloop_connection_delay) #uniform randomly assigned connection delay step value
-        self.timer = self.model.timer
-        self.node_connection_failure_percent = failure_percent
-        self.node_death_percent = death_percent
-        self.connection_failure = False
-        self.death = False
-        self.dkg_misbehaving = False
-        self.node_owner = int((np.random.normal(self.model.node_ownership_params[0], self.model.node_ownership_params[1])+3.5)*15) # picks an owner using the normal distribution and parameters set in the sim
-        self.malicious = self.model.owner_buckets[math.ceil(self.node_owner/10)] # sets the node as malicious if its owner is malicious
-
-    def step(self):
-        #simulate node failure
-        self.connection_failure = np.random.randint(0,100) < self.node_connection_failure_percent
-        self.death = np.random.randint (0,100) < self.node_death_percent
-
-        #disconnect the node if failure occurs
-        if (self.connection_failure or self.death) and self.connection_status == "connected":
-            self.node_disconnect()
-        else:
-            if self.connection_delay>0:
-                self.connection_delay -=1
-            else:
-                self.connection_status = "connected"
-                self.model.active_nodes[self.id] = self # add to the active nodes list
-                
-
-    def advance(self):
-        pass
-
-
-    def generate_tickets(self):
-        #generates tickets using the uniform distribution
-        self.ticket_list = np.random.random_sample(self.num_tickets)
-        
-    def node_disconnect(self):
[…]

### 2019-10-03 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/model.py

@@ -1,260 +1,0 @@
-from mesa import Model
-from mesa.time import SimultaneousActivation
-import agent
-import numpy as np
-from mesa.datacollection import DataCollector
-import logging as log
-import numpy as np
-import random as rnd
-import time
-
-class Beacon_Model(Model):
-    """The model"""
-    def __init__(self, nodes, ticket_distribution, active_group_threshold, 
-    group_size, max_malicious_threshold_percent, group_expiry, 
-    node_failure_percent, node_death_percent,
-    signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
-    log_filename, run_number, misbehaving_nodes, dkg_block_delay, compromised_threshold,
-    failed_signature_threshold, node_ownership_params):
-        self.num_nodes = nodes
-        self.schedule = SimultaneousActivation(self)
-        self.relay_request = False
-        self.active_groups = {}
-        self.num_active_groups = 0
-        self.active_nodes = {}
-        self.num_active_nodes = 0
-        self.inactive_nodes = []
-        self.active_group_threshold = active_group_threshold # number of groups that will always be maintained in an active state
-        self.max_malicious_threshold_percent = max_malicious_threshold_percent # threshold above which a signature is deemed to be compromised, typically 51%
-        self.group_size = group_size
-        self.ticket_distribution = ticket_distribution
-        self.newest_id = 0
-        self.group_expiry = group_expiry
-        self.bootstrap_complete = False # indicates when the initial active group list bootstrap is complete
-        self.group_formation_threshold = min_nodes # min nodes required to form a group
-        self.timer = 0
-        self.unsuccessful_signature_events = []
-        self.signature_delay = signature_delay
-        self.dkg_block_delay = dkg_block_delay
-        self.compromised_threshold = compromised_threshold
-        self.median_malicious_group_percents = 0
-        self.median_dominated_signatures_percents = 0
-        self.perc_dominated_signatures = 0
-        self.perc_compromised_groups = 0
-        self.total_signatures = 0
-        self.failed_signature_threshold = failed_signature_threshold
-        self.perc_failed_signatures = 0
-        self.node_ownership_params = node_ownership_params
-        self.owner_buckets = {i : np.random.randint(100)<30 for i in range(20)} 
-        self.datacollector = DataCollector(
-            model_reporters = {"# of Active Groups":"num_active_groups",
-             "# of Active Nodes":"num_active_nodes",
[…]

### 2019-10-03 Mesa Simulations/agent.py

@@ -126,9 +126,7 @@ class Group(Agent):
             if node.connection_status == "not connected": 
                 offline_count +=1
         return offline_count
-
     
-
 class Signature(Agent):
     def __init__(self, unique_id, model, group_object):
         super().__init__(unique_id, model)

### 2019-10-03 Mesa Simulations/agent.py
removed mainloop fork delay from agent

@@ -18,7 +18,6 @@ class Node(Agent):
         self.ticket_list = []
         self.connection_status = "not connected" #change later to event - currently used for node failure process
         self.connection_delay = np.random.randint(0,node_connection_delay) #uniform randomly assigned connection delay step value
-        self.mainloop_fork_delay = np.random.randint(0,node_mainloop_connection_delay) #uniform randomly assigned connection delay step value
         self.timer = self.model.timer
         self.node_connection_failure_percent = failure_percent
         self.node_death_percent = death_percent

### 2019-10-03 Mesa Simulations/agent.py
removed dkg_misbehaving var from node agent

@@ -23,7 +23,6 @@ class Node(Agent):
         self.node_death_percent = death_percent
         self.connection_failure = False
         self.death = False
-        self.dkg_misbehaving = False
         self.node_owner = int((np.random.normal(self.model.node_ownership_params[0], self.model.node_ownership_params[1])+3.5)*15) # picks an owner using the normal distribution and parameters set in the sim
         self.malicious = self.model.owner_buckets[math.ceil(self.node_owner/10)] # sets the node as malicious if its owner is malicious
 

### 2019-10-03 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
modified agent table to be for just one agent
deciding how to configure tabel
moved agent table to end of paper

@@
 ADD table for Agent types
-\begin{table}[htbp]
-    \caption{Agent Types}
-    \begin{center}
-    \begin{tabular}{|c|c|c|c|}
-    \hline
-    \textbf{Parameters}&\multicolumn{3}{|c|}{\textbf{Agents}} \\
-    \cline{2-4} 
-    \textbf{ } & \textbf{\textit{Node}}& \textbf{\textit{Group}}& \textbf{\textit{Signature}} \\
-    \hline
-    Unique ID & X & X & X \\
-    \hline
-    \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-    \end{tabular}
-    \label{table}
-    \end{center}
-    \end{table}
 
@@
 
+\newpage
+\begin{table}[htbp]
+    \caption{Node Agent}
+    \begin{center}
+    \begin{tabular}{|c|c|}
+    \cline{1-2} 
+    \textbf{Key Attributes}&{\textbf{Node Agent}} \\
+    \cline{1-2} 
+    \hline
+    Connection Delay & Delay between when a node is created and when it can join the network \\
+    Ticket List & List of random numbers used to pick the node for participation in a group\\
+    Connection Failure Percent & Likelihood of disconnecting from the network\\
+    Death Percent & Likelihood of going offline and never re-connecting\\
+    Malicousness & determines if a node is considered malicous based on if the operator is malicious\\
+    Operator  & the entity that runs this node\\
+    \hline
+    \textbf{ }&\textbf{Group Agent} \\
+    \multicolumn{2}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+    \end{tabular}
+    \label{table}
+    \end{center}
+    \end{table}
+
 \end{document}

### 2019-10-03 Mesa Simulations/agent.py
removed last signature variable

@@ -67,7 +67,6 @@ class Group(Agent):
         self.id = unique_id
         self.type = "group"
         self.members = members
-        self.last_signature = "none"
         self.status = "dkg" # status types: dkg, compromised, active, expired
         self.expiry = expiry # of steps before expiration
         self.timer = self.model.timer

### 2019-10-03 Mesa Simulations/agent.py
remove separate compromised % var from group agent

@@ -74,7 +74,6 @@ class Group(Agent):
         self.ownership_distr = []
         self.malicious_percent = 0
         self.offline_percent = 0
-        self.compromised_percent = 0
         self.process_complete = False
         self.dkg_block_delay = self.model.dkg_block_delay
 
@@ -89,7 +88,6 @@ class Group(Agent):
                 # based on DKG process we check for missing/malicious nodes 3 blocks before dkg completes
                 if self.dkg_block_delay == 3:
                     self.offline_percent = self.calculate_offline()/len(self.members) # calculates % nodes offline during dkg
-                    self.compromised_percent = self.malicious_percent #+ self.offline_percent
             else:
                 self.status = "active"
                 self.model.active_groups[self.id] = self # add to active groups list

### 2019-10-04 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
edited table, noticed agent and model were not cur

@@
     \textbf{ }&\textbf{Group Agent} \\
+    \hline
+    Members & list of nodes that are members of the group. Nodes can repeat \\
+    Expiry & number of blocks before group expires\\
+    Malicious Percent & percentage of the groups members that are malicious\\
+    Offline Percent & percentage of the groups members that are offline\\
+    DKG Delay & User set delay simulating the distributed key generation process during group creation\\
+    \hline
+    \textbf{ }&\textbf{Signature Agent} \\
+    \hline
+    Group & list of nodes that are members of the group. Nodes can repeat \\
+    Expiry & number of blocks before group expires\\
+    Delay &  user specified time between being triggered and being published on chain\\
+    Offline Percent & percentage of the groups members that are offline at the time of the signature\\
+    Lynchpin operator percent & percent of the group owned by a single operator\\
+    \hline
     \multicolumn{2}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}

### 2019-10-04 Mesa Simulations/agent.py
had to re-copy sim files from master

@@ -7,13 +7,12 @@ class Node(Agent):
     """ Node: One hardware device used to stake tokens on the network. 
     Each node will create virtual stakers proportional to
     the number of tokens owned by the node """
-    def __init__(self, unique_id, node_id, model, tickets, 
+    def __init__(self, unique_id, model, tickets, 
     failure_percent, death_percent, node_connection_delay,
-    node_mainloop_connection_delay, misbehaving_nodes):
+    node_mainloop_connection_delay, operator, malicious):
         super().__init__(unique_id, model)
         self.id = unique_id
         self.type = "node"
-        self.node_id = node_id
         self.num_tickets = int(tickets)
         self.ticket_list = []
         self.connection_status = "not connected" #change later to event - currently used for node failure process
@@ -23,8 +22,10 @@ class Node(Agent):
         self.node_death_percent = death_percent
         self.connection_failure = False
         self.death = False
-        self.node_owner = int((np.random.normal(self.model.node_ownership_params[0], self.model.node_ownership_params[1])+3.5)*15) # picks an owner using the normal distribution and parameters set in the sim
-        self.malicious = self.model.owner_buckets[math.ceil(self.node_owner/10)] # sets the node as malicious if its owner is malicious
+        self.dkg_misbehaving = False
+        self.node_operator = operator
+        self.malicious = malicious
+        self.model.newest_id +=1 # increments the model agent ID
 
     def step(self):
         #simulate node failure
@@ -40,11 +41,9 @@ class Node(Agent):
             else:
                 self.connection_status = "connected"
                 self.model.active_nodes[self.id] = self # add to the active nodes list
-                
 
     def advance(self):
         pass
-
 
     def generate_tickets(self):
         #generates tickets using the uniform distribution
@@ -60,13 +59,14 @@ class Node(Agent):
         if self.death == False: # does not reset the failure trigger if the death trigger is true
             self.failure = False
 
-class Group(Agent):
+class Signing_Group(Agent):
     """ A Group """
     def __init__(self, unique_id, model, members, expiry):
         super().__init__(unique_id, model)
         self.id = unique_id
         self.type = "group"
         self.members = members
+        self.last_signature = "none"
         self.status = "dkg" # status types: dkg, compromised, active, expired
         self.expiry = expiry # of steps before expiration
         self.timer = self.model.timer
@@ -74,9 +74,11 @@ class Group(Agent):
         self.ownership_distr = []
[…]

### 2019-10-04 Mesa Simulations/model.py

@@ -7,16 +7,17 @@ import logging as log
 import numpy as np
 import random as rnd
 import time
+import math
 
 class Beacon_Model(Model):
     """The model"""
-    def __init__(self, nodes, ticket_distribution, active_group_threshold, 
+    def __init__(self, stake_distribution, active_group_threshold, 
     group_size, max_malicious_threshold_percent, group_expiry, 
     node_failure_percent, node_death_percent,
     signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
-    log_filename, run_number, misbehaving_nodes, dkg_block_delay, compromised_threshold,
-    failed_signature_threshold, node_ownership_params):
-        self.num_nodes = nodes
+    log_filename, run_number, dkg_block_delay, compromised_threshold,
+    failed_signature_threshold, min_stake_amount, operator_mode, malicious_operator_percent):
+        self.num_nodes = 0
         self.schedule = SimultaneousActivation(self)
         self.relay_request = False
         self.active_groups = {}
@@ -27,8 +28,8 @@ class Beacon_Model(Model):
         self.active_group_threshold = active_group_threshold # number of groups that will always be maintained in an active state
         self.max_malicious_threshold_percent = max_malicious_threshold_percent # threshold above which a signature is deemed to be compromised, typically 51%
         self.group_size = group_size
-        self.ticket_distribution = ticket_distribution
-        self.newest_id = 0
+        self.stake_distribution = stake_distribution
+        self.newest_id = 0 #ID count for agents
         self.group_expiry = group_expiry
         self.bootstrap_complete = False # indicates when the initial active group list bootstrap is complete
         self.group_formation_threshold = min_nodes # min nodes required to form a group
@@ -44,16 +45,16 @@ class Beacon_Model(Model):
         self.total_signatures = 0
         self.failed_signature_threshold = failed_signature_threshold
         self.perc_failed_signatures = 0
-        self.node_ownership_params = node_ownership_params
-        self.owner_buckets = {i : np.random.randint(100)<30 for i in range(20)} 
+        self.number_of_owners = len(stake_distribution)
+        self.min_stake_amount = min_stake_amount
         self.datacollector = DataCollector(
             model_reporters = {"# of Active Groups":"num_active_groups",
              "# of Active Nodes":"num_active_nodes",
              "# of Signatures":"total_signatures",
              "Median Malicious Group %": "median_malicious_group_percents",
              "% Compromised Groups": "perc_compromised_groups",
[…]

### 2019-10-21 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added results for multi-run linear

@@
 
-\subsection{How could node failures affect system behavior?}
+\subsection{How could node failures and group sizes affect system behavior?}
 Nodes may go offline or fail entireley. Since their participation in groups is critical to the 
@@
 
-\subsection{Effects of Node failures on group and signature characteristics}
-To evaluate the possible effects of node failure on group and signature characteristics, we use the
-multi-run study. We then observe trends in the specific parameters discussed below.
+\subsection{Effects of Node failures, Group Size and Stake Distributions}
+To evaluate the possible effects of node failure and stake distributions on group and signature 
+characteristics, we use the multi-run study. We then observe trends in the specific parameters 
+discussed below. We also run each multi run study for each of the three distribitions to study 
+the correlation between the observed trends and the type of stake distribution.
 
-\subsection{Effects of stake distributions on group and signature characteristics}
+    Using the \textit{linear distribution:}
+
+        \begin{table}[htbp]
+            \caption{Lynchpinned Signatures}
+            \begin{center}
+            \begin{tabular}{|c|c|c|c|}
+            \hline
+            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
+            \cline{2-4} 
+            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
+            \hline
+            5 &  0.006065 &  0.000000 &  0.000000 \\
+            \hline
+            10 &  0.071656 &  0.009276 &  0.003985 \\
+            \hline
+            20 &  0.399020 &  0.262837 &  0.177465 \\
+            \hline
+            \end{tabular}
+            \label{lynchpinned_table1}
+            \end{center}
+        \end{table}
+
+        \begin{table}[htbp]
+            \caption{Compromised Groups}
+            \begin{center}
+            \begin{tabular}{|c|c|c|c|}
+            \hline
+            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
+            \cline{2-4} 
+            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
+            \hline
+            5 &  0.590035 &  0.435403 &  0.407054 \\
+            \hline
+            10 &  0.428957 &  0.710509 &  0.536904 \\
+            \hline
+            20 &  0.557832 &  0.591663 &  0.555565 \\
+            \hline
+            \end{tabular}
+            \label{compromised_table1}
+            \end{center}
+        \end{table}
+
+        \begin{table}[htbp]
+            \caption{Failed Signatures}
+            \begin{center}
+            \begin{tabular}{|c|c|c|c|}
+            \hline
+            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
+            \cline{2-4} 
+            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
+            \hline
+            5 &  0.0 &  0.0 &  0.0 \\
+            \hline
+            10 &  0.0 &  0.0 &  0.0 \\
+            \hline
+            20 &  0.0 &  0.0 &  0.0 \\
+            \hline
+            \end{tabular}
+            \label{failed_table1}
+            \end{center}
+        \end{table}
+
+        Using the \textit{Ethereum distribution:}
 
@@
 
+\newpage
 \begin{figure*}[h]
@@
     \end{tabular}
-    \label{table}
+    \label{agent_table}
     \end{center}

### 2019-10-21 Mesa Simulations/analysis.py
Name thresholds explicitly
Change `max_malicious` in the analysis variables to `bls_threshold`.
Name and calculate various thresholds explicitly:

- `shares_required`, previously `min_honest`
- `compromise_threshold`
- `failure_threshold`

This also makes lynchpin calculations a bit clearer.

@@ -3,7 +3,6 @@ import numpy as np
 from scipy import stats
 
 
-
 class Beacon_Analysis():
     """Analytical solutions for simulation questions"""
     def __init__(
@@ -16,10 +15,8 @@ class Beacon_Analysis():
 
             # number of members in a group
             group_size,
-            # threshold of the BLS signature:
-            #   producing a signature requires `(max_malicious + 1)` shares
-            #   and tolerates up to `max_malicious` malicious members
-            max_malicious,
+            # threshold of the BLS signature
+            bls_threshold,
 
             # fraction of nodes that are offline at any given moment
             node_failure_probability,
@@ -30,8 +27,17 @@ class Beacon_Analysis():
         self.malicious_virtual_stakers = floor(virtual_stakers * adversary_power)
 
         self.group_size = group_size
-        self.max_malicious = max_malicious
-        self.min_honest = max_malicious + 1
+
+        # the minimum number of shares required for a signature to be produced
+        self.shares_required = bls_threshold + 1
+
+        # the maximum number of members
+        # that can collude without compromising the group
+        self.compromise_threshold = bls_threshold
+
+        # the maximum number of members
+        # that can be absent from signature generation without failure
+        self.failure_threshold = group_size - (self.shares_required)
 
         self.p_failure = node_failure_probability
         self.p_death = node_death_probability
@@ -101,7 +107,8 @@ class Beacon_Analysis():
         # build a custom discrete distribution
         nk = self.g_range()
         pk = self.inactive()
-        dist = stats.rv_discrete(name='inactive', values=(nk, pk))
+        dist = stats.rv_discrete(name='inactive',
+                                 values=(nk, pk))
 
         return dist
 
@@ -110,23 +117,23 @@ class Beacon_Analysis():
         # A group is compromised if the number of malicious members
         # exceeds the maximum number of malicious members:
         #
-        #     n_malicious > max_malicious
+        #     n_malicious > compromise_threshold
         #
         dist = self.malicious_dist()
 
-        return dist.sf(self.max_malicious)
+        return dist.sf(self.compromise_threshold)
 
 
     def sigfail(self):
         # A signature cannot be produced if the number of online members
         # is less than the minimum number of honest members:
         #
-        #     group_size - n_inactive < min_honest
-        #     n_inactive > group_size - min_honest
+        #     group_size - n_inactive < shares_required
[…]

### 2019-10-22 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added eth distr multi-run results
added to intro and changed table titles

@@
 of tools and processes. As such, ABM lends itself well to analyzing these systems
-to support the design process and evaluate system state after launch.
+to support the design process and evaluate system state after launch. In many situations,
+agent based modeling maybe the only method to evaluate a cryptoeconomic system as many are
+opaque and do not generate significant visible data. Similar to the field of astronomy, an
+agent based model could be used to replicate observable system behavior and then infer
+causes.
 
@@
 
-    Using the \textit{linear distribution:}
+\textit{Group Size} in all distributions group size appears to reduce the percentage
+of lynchpinned signatures and compromised groups. why?
 
-        \begin{table}[htbp]
-            \caption{Lynchpinned Signatures}
+\textit{Failure percent}
+
+        \begin{table}[h!]
+            \caption{Linear Distribution - Lynchpinned Signatures}
             \begin{center}
@@
 
-        \begin{table}[htbp]
-            \caption{Compromised Groups}
+        \begin{table}[h!]
+            \caption{Linear Distribution - Compromised Groups}
             \begin{center}
@@
 
-        \begin{table}[htbp]
-            \caption{Failed Signatures}
+        \begin{table}[h!]
+            \caption{Linear Distribution - Failed Signatures}
             \begin{center}
@@
 
-        Using the \textit{Ethereum distribution:}
+        \begin{table}[h!]
+            \caption{Ethereum distribution - Lynchpinned Signatures}
+            \begin{center}
+            \begin{tabular}{|c|c|c|c|}
+            \hline
+            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
+            \cline{2-4} 
+            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
+            \hline
+            5 &  0.011012 &  0.000000 &  0.000000 \\
+            \hline
+            10 &  0.073725 &  0.025947 &  0.006042 \\
+            \hline
+            20 &  0.407753 &  0.325947 &  0.203095 \\
+            \hline
+            \end{tabular}
+            \label{lynchpinned_table2}
+            \end{center}
+        \end{table}
 
+        \begin{table}[h!]
+            \caption{Ethereum distribution - Compromised Groups}
+            \begin{center}
+            \begin{tabular}{|c|c|c|c|}
+            \hline
+            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
+            \cline{2-4} 
+            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
+            \hline
+            5 &  0.592699 &  0.383390 &  0.394198 \\
+            \hline
+            10 &  0.566964 &  0.616098 &  0.683071 \\
+            \hline
+            20 &  0.549456 &  0.526661 &  0.454106 \\
+            \hline
+            \end{tabular}
+            \label{compromised_table2}
+            \end{center}
+        \end{table}
+
+        \begin{table}[h!]
+            \caption{Ethereum distribution - Failed Signatures}
+            \begin{center}
+            \begin{tabular}{|c|c|c|c|}
+            \hline
+            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
+            \cline{2-4} 
+            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
+            \hline
+            5 &  0.0 &  0.0 &  0.0 \\
+            \hline
+            10 &  0.0 &  0.0 &  0.0 \\
+            \hline
+            20 &  0.0 &  0.0 &  0.0 \\
+            \hline
+            \end{tabular}
+            \label{failed_table2}
+            \end{center}
+        \end{table}
+
+\newpage
 \section{Conclusion and Future work}

### 2019-10-24 Mesa Simulations/model.py
found some dominated and chaned to lynchpinned

@@ -39,8 +39,8 @@ class Beacon_Model(Model):
         self.dkg_block_delay = dkg_block_delay
         self.compromised_threshold = compromised_threshold
         self.median_malicious_group_percents = 0
-        self.median_dominated_signatures_percents = 0
-        self.perc_dominated_signatures = 0
+        self.median_lynchpinned_signatures_percents = 0
+        self.perc_lynchpinned_signatures = 0
         self.perc_compromised_groups = 0
         self.total_signatures = 0
         self.failed_signature_threshold = failed_signature_threshold
@@ -237,8 +237,8 @@ class Beacon_Model(Model):
                 failed_signatures += (signature.offline_percent>=self.failed_signature_threshold)
 
         self.perc_failed_signatures = failed_signatures/(total_signatures+0.00000000000000001)
-        self.median_dominated_signatures_percents = np.median(lynchpin_array)
-        self.perc_dominated_signatures = lynchpin_count/(total_signatures+0.00000000000000001)
+        self.median_lynchpinned_signatures_percents = np.median(lynchpin_array)
+        self.perc_lynchpinned_signatures = lynchpin_count/(total_signatures+0.00000000000000001)
         self.total_signatures = total_signatures
 
 

### 2019-10-24 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added conclusion

@@
 discussed below. We also run each multi run study for each of the three distribitions to study 
-the correlation between the observed trends and the type of stake distribution.
+the correlation between the observed trends and the type of stake distribution. Additionally, byzantine
+taking the median measures of each variable, we hope to address the fluctuations due to distributions with
+increased centralization.
 
 \textit{Group Size} in all distributions group size appears to reduce the percentage
-of lynchpinned signatures and compromised groups. why?
+of lynchpinned signatures and compromised groups. Intuitively this makes since since 
+as we increase the size of a group, we include more group owners who may not be malicious. 
+comment on degree of change?
 
-\textit{Failure percent}
+\textit{Node Failure percent} appears to significantly impact the lynchpinned signature percentage
+but have little to no effect on compromised groups. Why?
+
+\textit{Distribution} centralization appears to minimally affect these trends but, it is very likeley
+that the use of the median for each run is the cause of this. We would expect that highly centralized
+distributions would cause fluctuations in these values similar to their effect on the final steady state 
+level. This is primarily due to the ownership of a larger number of nodes by a few operators in highly 
+centralized distributions.
 
@@
 \section{Conclusion and Future work}
-\begin{itemize}
-\item Dynamic systems -Transfer functions instead of stochastic representations?
-\item Utility functions
-\item Genetic Algorithms
-\item Additional questions
-\end{itemize}
+This theoretical analysis highlighted possible behaviors of the Keep network beacon. we
+validated the model using some simple analytical methods. However, once the beacon launches
+we can use real data from the network to validate and adjust the model. At this point we can
+then use the model to better investigate future behaviours and causes of behavior.
 

### 2019-10-24 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
discussed the klages-mundt paper

@@
 markus@keep.network}
-
-\and
-\IEEEauthorblockN{Liam Zebedee}
-\IEEEauthorblockA{\textit{Keep Network} \\
-liam@keep.network}
 }
@@
 \section{Analysis of Token based systems}
+Klages-Mundt et al.\cite{klages2019stability} use agent based models to simulate a decentralized stable coin
+system and shows how deleveraging sprial attacks could occur. Their model is also able
+to explain real complex stable coin movements. Further, the study is able
+to show theoretically that regions of stability and instability exist for such decentralized
+stable coin systems.
 
-Discuss the use of ABM for token engineering. Cite recent papers.
+While not agent based, Chitra et al. \cite{chitra2019agent} effectively use discrete event simuation to
 
@@
 
-\textit{Percent Lynchpinned Signatures}
+\textit{Percent Lynchpinned Signatures} Why does this not fluctuate as much?
 

### 2019-10-24 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added chitra reference

@@
 
-While not agent based, Chitra et al. \cite{chitra2019agent} effectively use discrete event simuation to
-
-Agent based systems could help evaluate trends in behavior related to
-various system parameters. They may not however, accurateley represent 
-actual system performance.
+While not agent based, Chitra et al. \cite{chitra2019agent} effectively use discrete event simuation to provide
+quantitative estimates of how economic incentives affect security. They use a custom simulation
+environment to simulate Kadena's Chainweb, and provide insights into how simulation can guide
+and optimize protocol development in a variety of contexts.
 
 Discuss levels of complexity, with citations. Why greater complexity may
-not get you much more insight.
+not get you much more insight. (ask Shruti?)
 

### 2019-10-25 Mesa Simulations/model.py
added operator_lynchpin_percent

@@ -226,14 +226,18 @@ class Beacon_Model(Model):
 
     def calculate_lynchpinned_signatures(self):
         lynchpin_array = []
+        owner_lynchpin_array = []
         lynchpin_count = 0
+        owner_lynchpin_count = 0
         total_signatures = 0
         failed_signatures = 0
         for signature in self.schedule.agents:
             if signature.type == "signature":
                 total_signatures +=1
-                lynchpin_array.append(signature.lynchpin_percent)
+                lynchpin_array.append(signature.owner_lynchpin_percent)
+                owner_lynchpin_array.append(signature.owner_lynchpin_percent)
                 lynchpin_count += (signature.lynchpin_percent>=self.max_malicious_threshold_percent)
+                owner_lynchpin_count += (signature.owner_lynchpin_percent>=self.max_malicious_threshold_percent)
                 failed_signatures += (signature.offline_percent>=self.failed_signature_threshold)
 
         self.perc_failed_signatures = failed_signatures/(total_signatures+0.00000000000000001)

### 2019-10-25 Mesa Simulations/agent.py
changed owner reference to operator

@@ -147,7 +147,7 @@ class Signature(Agent):
         self.block_delay_complete = False
         self.lynchpin_percent = 0
         self.offline_percent = 0
-        self.owner_lynchpin_percent = 0
+        self.operator_lynchpin_percent = 0
 
         self.model.newest_id +=1 # increments the model agent ID by 1 after a new signature is created 
 
@@ -189,7 +189,7 @@ class Signature(Agent):
                 except:
                     shares_by_staker.update({self.model.active_nodes[node_id].node_operator : node_tickets})
                     
-        self.owner_lynchpin_percent = shares_by_staker[max(shares_by_staker)]/total_tickets
+        self.operator_lynchpin_percent = shares_by_staker[max(shares_by_staker)]/total_tickets
 
     
 

### 2019-10-25 Mesa Simulations/model.py

@@ -226,18 +226,18 @@ class Beacon_Model(Model):
 
     def calculate_lynchpinned_signatures(self):
         lynchpin_array = []
-        owner_lynchpin_array = []
+        operator_lynchpin_array = []
         lynchpin_count = 0
-        owner_lynchpin_count = 0
+        operator_lynchpin_count = 0
         total_signatures = 0
         failed_signatures = 0
         for signature in self.schedule.agents:
             if signature.type == "signature":
                 total_signatures +=1
                 lynchpin_array.append(signature.owner_lynchpin_percent)
-                owner_lynchpin_array.append(signature.owner_lynchpin_percent)
+                operator_lynchpin_array.append(signature.operator_lynchpin_percent)
                 lynchpin_count += (signature.lynchpin_percent>=self.max_malicious_threshold_percent)
-                owner_lynchpin_count += (signature.owner_lynchpin_percent>=self.max_malicious_threshold_percent)
+                operator_lynchpin_count += (signature.operator_lynchpin_percent>=self.max_malicious_threshold_percent)
                 failed_signatures += (signature.offline_percent>=self.failed_signature_threshold)
 
         self.perc_failed_signatures = failed_signatures/(total_signatures+0.00000000000000001)

### 2019-10-28 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
fixed issue with missing coloumn
added hypergeometric to analytical group selection

@@
 \section{Verification and Validation}
-Benchmark using analytical methods - from Promethea
+Where possible, we use analytical methods to verify aspects of the sim. In the absence of 
+real world data, this is our best way to increase confidence in simulation results.
+
+\subsection{Group Selection}
+We model group selection using a hypergeometric distribution. For our purposes, we assume the n draws to 
+be the equivalent of selecting a group of n members, with k members being malicious. We draw the sample from
+a population of N virtual stakers, with K stakers being malicious.
+
+\begin{equation}
+    Pr(X = k) = \frac{{K \choose k} {N-K\choose n-k}}{{N \choose n}}
+\end{equation}
+
+Show analytical results in comparison with simulation
 
@@
 
-\newpage
 \section{Conclusion and Future work}
@@
 
+\newpage
 \bibliographystyle{plain}

### 2019-10-28 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
edited effects of failure on compromised groups

@@
 
-Show analytical results in comparison with simulation
+Show analytical results in comparison with simulation?
+
+\subsection{Compromised Groups}
+We use the survival function of the hypergeometric distribution to determine
+the likelihood of a group of n members being compromised. To do this we evaluate
+the function at the max malicious threshold. (in the sim we have a separate compromised threshold)
+
+\subsection{Node Attrition, Failures, and Inactivity}
+We model Node attrition and failures as Binomial, and Inactivity as a function of 
+the two.
+
+Describe mathematically....
+
+\subsection{Lynchpinned Signatures}
+
+\subsection{Failed Signatures}
 
@@
 \subsection{Convergence pressures}
-
 The model primarily converges to steady state due to factors such as
@@
 \textit{Group Size} in all distributions group size appears to reduce the percentage
-of lynchpinned signatures and compromised groups. Intuitively this makes since since 
-as we increase the size of a group, we include more group owners who may not be malicious. 
+of lynchpinned signatures but have no impact on compromised groups. Our defininition of compromised
+groups is independent of node failure's and therefore the variation shown is likeley not related to
+node failure.
+
 comment on degree of change?
@@
 
-\section{Conclusion and Future work}
+\newpage
+\section{Conclusion and Future work}[h!]
 This theoretical analysis highlighted possible behaviors of the Keep network beacon. we

### 2019-11-05 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
making changes to match analytical

@@
     state behavior, at which point we evaluate the sensitivity of specific 
-    group and signature characteristics to various parameters. The results 
-    of this study illustrates the effectiveness of ABM as an aid to the design 
-    of novel distributed systems.
+    group and signature characteristics to various parameters. This study 
+    illustrates the effectiveness of ABM as an aid to the design 
+    of novel distributed systems. The team also intends to use this simulation
+    as a way to analyze Keep system behavior after launch.
 
@@
 the likelihood of a group of n members being compromised. To do this we evaluate
-the function at the max malicious threshold. (in the sim we have a separate compromised threshold)
+the function at the max malicious threshold.
 

### 2019-11-05 Mesa Simulations/agent.py

@@ -125,7 +125,6 @@ class Signing_Group(Agent):
                 temp_malicious_count +=1
         self.malicious_percent = temp_malicious_count/sum(self.ownership_distr)
 
-
     def calculate_offline(self):
         offline_count = 0
         for node in self.members:

### 2019-11-05 Mesa Simulations/model.py

@@ -15,7 +15,7 @@ class Beacon_Model(Model):
     group_size, max_malicious_threshold_percent, group_expiry, 
     node_failure_percent, node_death_percent,
     signature_delay, min_nodes, node_connection_delay, node_mainloop_connection_delay, 
-    log_filename, run_number, dkg_block_delay, compromised_threshold,
+    log_filename, run_number, dkg_block_delay,
     failed_signature_threshold, min_stake_amount, operator_mode, malicious_operator_percent):
         self.num_nodes = 0
         self.schedule = SimultaneousActivation(self)
@@ -37,7 +37,6 @@ class Beacon_Model(Model):
         self.unsuccessful_signature_events = []
         self.signature_delay = signature_delay
         self.dkg_block_delay = dkg_block_delay
-        self.compromised_threshold = compromised_threshold
         self.median_malicious_group_percents = 0
         self.median_lynchpinned_signatures_percents = 0
         self.perc_lynchpinned_signatures = 0
@@ -53,8 +52,8 @@ class Beacon_Model(Model):
              "# of Signatures":"total_signatures",
              "Median Malicious Group %": "median_malicious_group_percents",
              "% Compromised Groups": "perc_compromised_groups",
-             "Median Lynchpin %":"median_dominated_signatures_percents",
-             "% Lynchpinned signatures":"perc_dominated_signatures",
+             "Median Lynchpin %":"median_lynchpinned_signatures_percents",
+             "% Lynchpinned signatures":"perc_lynchpinned_signatures",
              "Failed Singature %" : "perc_failed_signatures" },
             agent_reporters={"ID": "id" , 
             "Type" : "type",
@@ -222,7 +221,7 @@ class Beacon_Model(Model):
                 total_groups +=1
                 malicious_array.append(group.malicious_percent) #creates an array of malicious percents for each group
         self.median_malicious_group_percents = np.median(malicious_array)
-        self.perc_compromised_groups = sum(np.array(malicious_array)>=self.compromised_threshold)/(total_groups+0.000000000000000001)
+        self.perc_compromised_groups = sum(np.array(malicious_array)>=self.max_malicious_threshold_percent)/(total_groups+0.000000000000000001)
 
     def calculate_lynchpinned_signatures(self):
         lynchpin_array = []
@@ -234,7 +233,7 @@ class Beacon_Model(Model):
         for signature in self.schedule.agents:
             if signature.type == "signature":
                 total_signatures +=1
[…]

### 2019-11-05 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added hypergeometric figure and edited compr expl

@@
 be the equivalent of selecting a group of n members, with k members being malicious. We draw the sample from
-a population of N virtual stakers, with K stakers being malicious.
+a population of N virtual stakers, with K stakers being malicious. For example, 
+\ref{fig: hypergeometric_distribution} shows a distribution for a group of 100 stakers. 
+Based on this distribution we would expect that the number of malicous stakers in this group
+would be between approx 20-40 stakers.
 
@@
 
-Show analytical results in comparison with simulation?
+\begin{figure}[h!]
+    \includegraphics[width=\linewidth]{hypergeometric.png}
+    \caption{Linear Stage Distribution}
+    \label{fig: hypergeometric_distribution}
+\end{figure}
 
@@
 the likelihood of a group of n members being compromised. To do this we evaluate
-the function at the max malicious threshold.
+the function at the max malicious threshold. Using our example above, we would
+expect the percentage of compromised groups to be approximateley 50 percent
+for a threshold of 25 percent.
 

### 2020-02-25 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex

@@
 promethea@keep.network}
-
-\and
-\IEEEauthorblockN{Markus Fix}
-\IEEEauthorblockA{\textit{Keep Network} \\
-markus@keep.network}
 }
@@
 \begin{abstract}
-    ABM is an effective tool for analysis of complex systems with long term 
-    emergent behavior. In this study we apply ABM to analyse the long term 
-    behavior of Keep’s random beacon. We look for the emergence of steady 
-    state behavior, at which point we evaluate the sensitivity of specific 
-    group and signature characteristics to various parameters. This study 
-    illustrates the effectiveness of ABM as an aid to the design 
-    of novel distributed systems. The team also intends to use this simulation
-    as a way to analyze Keep system behavior after launch.
+    Agent Based Modeling (ABM) is an effective tool for analysis of complex systems with long term  emergent behavior.
+Distributed systems that rely on token economics are such complex systems.
+The behavior of these systems is difficult to predict due to the the interaction of various agents with different incentives.
+In particular, agents with malicious motives could compromise the integrity of the system, and agent based modeling can help forecast possible attack scenarios.
+In this study we apply ABM to analyze the long term behavior of Keep’s random beacon, which uses a threshold relay to generate and sign random numbers.
+The threshold relay is comprised of nodes that form groups which utilize a distributed key to sign each random number transaction.
+Nodes participate in groups by staking the Keep token, but since this is not a permissioned system nodes could be malicious and seek to compromise the integrity of the generated random number.
+The goals of the simulation are to look for the emergence of steady state behavior, at which point we evaluate the sensitivity of specific group and signature characteristics to maliciousness.
+In particular we evaluate the impact of various token maliciousness on the successful creation of a signature.
+We attempt to verify and validate the sim using some analytical forecasting methods.
+This study illustrates the effectiveness of ABM as an aid to the design of novel distributed systems.
+The team also intends to use this simulation as a way to analyze Keep system behavior after launch.
 
@@
 Discuss levels of complexity, with citations. Why greater complexity may
-not get you much more insight. (ask Shruti?)
+not get you much more insight.
 
